---
title: "Renewvia - Survey Impact Analysis"
# output:
#   html_document:
#     df_print: paged
#   pdf_document: default
output:
html_notebook: default
---

# Overview

## Descriptive

-   Summary statistics

-   Visualization with graphs/charts

## **Inferential**

-   For the paired data set, we will use the following

    -   Paired t-Test for ratio

    -   Wilcoxon Signed Rank Test (Sign Test if asymmetric) for ordinal variables

    -   McNemar Test for Pre-Post binary responses

-   Our independent variables will be at two levels:

    -   Community: PV Size (kWh), No. of Customers, CAPEX (USD)

    -   Individual: Avg. Monthly Energy Consumption (kWh)

-   For each dependent variables, we will run a uni-variate regression tests with each of independent variable. When applicable, we will have a Linear regression t-Test or Logistic regression Wald test

# Libraries

```{r results='hide', message=FALSE, warning=FALSE}
# Importing libraries
options(warn=-1)
library(ggplot2)
library(dplyr)
library(lessR)
library(tidyr)
library(ggpubr)
library(exact2x2)
library(stringr)
library(epiDisplay)
library(tibble)
library(ggExtra)
library(vtree)
library(CGPfunctions)
library(psych)
library(nonpar)
library(scales)
library(tidyverse)
library(ggrepel)
library(data.table)
library(forcats)
library(glue)
library(aod)
library(datawizard)
library(caret)
library(purrr)
library(Hmisc)
library(corrplot)
library(rempsyc)
library(vioplot)
library(ggthemes)
library(lmtest)
library(cowplot)
library(latex2exp)
library(rstatix)
library(glue)
```

# Input Data

## Community

```{r}
## Locading the project& consumption data
consumption_period <- read.csv("consumption_period.csv")
consumption_all <- read.csv("consumption_cumulative.csv")
customer_info <- read.csv("customers_info.csv")

tmp <- merge(customer_info, consumption_period, 
              by.x = 'customerAccountNumber',
              by.y = 'Account.Number')  
temp <- merge(tmp, consumption_all, 
              by.x = 'customerAccountNumber',
              by.y = 'Customer.Account.Number')
# temp_group <- temp %>% 
#                     group_by(projectName) %>% 
#                     summarise(consumption = sum(Energy.Consumption, na.rm=TRUE))
projects <- read.csv("project_data.csv")
# projects <- merge(projects, temp_group, by.x="project_name", by.y="projectName")
```

## Survey Clean Data sets

### Households

```{r}
## Intial Survey
initial <- read.csv("data_cleaning/datasets_clean/initial_clean.csv",
                          na.strings=c("","NA"))
initial_clean <- merge(initial, customer_info, 
                     by.x = 'renewvia_id', 
                     by.y = 'customerAccountNumber') %>% 
                    filter(tariff == "Residential")
# Pre-connection
initial_pre <- initial_clean %>%
                    filter(status == "pre_connection")

write.csv(initial_pre, "initial_pre.csv", row.names=FALSE)
# Post-connection
initial_post <- initial_clean %>%
                    filter(status == "post_connection") 

## Household Post-Survey
post <- read.csv("data_cleaning/household_post_survey_anonymized.csv"
                          #na.strings=c("","NA")
                 )
# post_clean <- merge(post, temp,
#                        by.x = 'renewvia_id',
#                        by.y = 'customerAccountNumber')%>%
#                     filter(tariff == "Residential")
# 
# write.csv(post_clean, "post_clean.csv", row.names=FALSE)
## Pairing pre and post responses
paired_clean <- merge(initial_pre, post,
                      suffix = c("_pre", "_post"),
                      by= 'renewvia_id')
nigeria_paired_clean <- paired_clean %>% 
                                filter(country_pre == "nigeria")
#income_rectified <- read.csv("kenya_incomes_rectified.csv")
# paired_clean <- merge(paired_clean, income_rectified,
#                           by.x = 'renewvia_id', 
#                           by.y = 'Customer.Account.Number')
# write.csv(paired_clean, file='paired_clean.csv',
#           fileEncoding = "UTF-8")
```

### Commercial & Institution

```{r}
## Commercial & Insitution Post-Survey
ci <- read.csv("data_cleaning/datasets_clean/ci_post_clean.csv",
                          na.strings=c("","NA"))
ci$renewvia_id <- toupper(ci$renewvia_id)
ci_clean <- merge(ci, temp,
                       by.x = 'renewvia_id', 
                       by.y = 'customerAccountNumber')
write.csv(ci_clean, "ci_clean.csv", row.names=FALSE)
# head(ci_clean)
# Org Type
schools_clean <- ci_clean %>% filter(business_type == "school")
business_clean <- ci_clean %>% filter(business_type == "shop" | 
                                        business_type == "other_business")
institut_clean <- ci_clean %>% filter(business_type == "religious_institution")
clinic_clean <- ci_clean %>% filter(business_type == "clinic")
```

## Survey Encoded Data sets

### Households

```{r}
## Locading the encoded data sets
# Intial Survey
initial_enc <- read.csv("data_cleaning/datasets_encoded/initial_encoded.csv",
                          na.strings=c("","NA")) 
initial_enc <- merge(initial_enc, customer_info, 
                     by.x = 'renewvia_id', 
                     by.y = 'customerAccountNumber') %>% 
                    filter(tariff == "Residential")
# Pre-connection
initial_pre_enc <- initial_enc %>%
                    filter(status == 0)
# Pre-connection
initial_post_enc <- initial_enc %>%
                    filter(status == 1)

# Household Post-Survey
post <- read.csv("data_cleaning/datasets_encoded/post_encoded.csv",
                          na.strings=c("","NA"))
post_enc <- merge(post, temp,
                       by.x = 'renewvia_id', 
                       by.y = 'customerAccountNumber')  %>% 
                    filter(tariff == "Residential")

paired_enc <- merge(initial_pre_enc, post_enc,
                      suffix = c("_pre", "_post"),
                      by= 'renewvia_id')

nigeria_paired_enc <- paired_enc %>% filter(country_pre == 1)
kenya_paired_enc <- paired_enc %>% filter(country_pre == 2)
kenya_paired_enc <- kenya_paired_enc[, !names(kenya_paired_enc) %in% c("avg_household_income_post")]
# Rectified incomes
income_rectified <- read.csv("kenya_incomes_rectified.csv")
kenya_paired_enc <- merge(kenya_paired_enc, income_rectified,
                          by.x = 'renewvia_id',
                          by.y = 'Customer.Account.Number')
```

```{r}
write.csv(kenya_paired_enc, "kenya_paired_enc.csv", row.names=FALSE)
write.csv(nigeria_paired_enc, "nigeria_paired_enc.csv", row.names=FALSE)
```

### Commercial & Institution

```{r}
# Commercial & Insitution Post-Survey
ci <- read.csv("data_cleaning/datasets_encoded/ci_post_encoded.csv",
                          na.strings=c("","NA")) 
ci$renewvia_id <- toupper(ci$renewvia_id)
ci_enc <- merge(ci, temp,
                 by.x = 'renewvia_id', 
                 by.y = 'customerAccountNumber')

# Org Type
schools_enc <- ci_enc %>% filter(business_type == 3)
business_enc <- ci_enc %>% filter(business_type == 2 | business_type == 5)
institut_enc <- ci_enc %>% filter(business_type == 4)
clinic_enc <- ci_enc %>% filter(business_type == 1)
```

# Utility Functions

## Remove Outliers

```{r}
outliers_removal <- function(data, var) {
  quartiles <- quantile(data[, var], 
                        probs=c(.25, .75), na.rm = TRUE)
  
  IQR <- IQR(data[, var], na.rm = TRUE)
  
  Lower <- quartiles[1] - 1.5*IQR
  Upper <- quartiles[2] + 1.5*IQR 
  
  data <- subset(data, 
                 data[, var] > Lower &
                 data[, var] < Upper)
  return(data)
}
```

## Descriptive

```{r}
get_stats <- function(data_source, var_name,
                      remove_outliers = FALSE, 
                      exclude_zeros = FALSE) {
  if (remove_outliers == TRUE) {
    data <- outliers_removal(data=data_source, var=var_name)
  } 
  
  var <- data[, var_name]
  
  if (exclude_zeros == TRUE) {
    print("Removing Zeros")
    var <- var[var != 0]
  } 
  
  stats <- t(describe(var, IQR=TRUE, quant=c(.1,.25,.5,.75,.90),))
  print(t.test(var, conf.level = 0.95))
  print(stats)
}
```

## Data Visualization

### Remove x and y axes

```{r}
# Remove y-axis if deemed redundant
remove_y <- theme(
  axis.text.y = element_blank(),
  axis.ticks.y = element_blank(),
  axis.title.y = element_blank()
)
# Remove x-axis if deemed redundant
remove_x <- theme(
  axis.text.x = element_blank(),
  axis.ticks.x = element_blank(),
  axis.title.x = element_blank()
)
```

### Plotting Graphs/Charts

```{r}
# For bar_simple and bar charts
plot_func <- function(df, var_name, var_type, 
                      plot_title, lgd, plot_type, 
                      char_remove=NULL,
                      remove_outliers = FALSE,
                      x_axis=NULL, y_axis=NULL) {
  if(is.null(char_remove) == FALSE) {
    df <- df %>% filter(!.data[[var_name]] %in% char_remove)
  }
  
  if(remove_outliers == TRUE) {
      df <- outliers_removal(data=df, var=var_name)
  }
  
  if(var_type == "non_cont") {
      var <- df[, var_name]
      var <- var[var != ""]
      
      data <- as.data.frame(t(table(var)))[,2:3] 
      setnames(data, 
               old = c('var','Freq'), 
               new = c('labels','counts'))
      # print(data)
      data_tab <- data %>% mutate(csum = rev(cumsum(rev(counts))),
                       pos = counts/2 + lead(csum, 1),
                       pos = if_else(is.na(pos), counts/2, pos),
                       percentage = counts/sum(counts))
      data_tab$labels <- as.factor(data_tab$labels)
      print(data_tab)
      if (plot_type == 'pie') {
          plot <- data_tab %>% ggplot(aes(x = "", y = counts, 
                                          fill = labels)) +
                              geom_col(width = 1, color = 1) +
                              geom_label_repel(
                                aes(y = pos,
                                    label = glue("{counts} ({percent(percentage)})"),
                                     fill = labels),
                                    show.legend = FALSE) +
                              labs(fill = lgd, title=plot_title) +
                              coord_polar(theta = "y") +
                              theme_void() + 
                              theme(legend.text=element_text(size=6))
      } else if (plot_type == "bar_simple") {
          plot <- data_tab %>% ggplot(aes(y=percentage,
                                      x=labels,
                                      fill=labels)) +
                            geom_col(width = 0.7) 
                            labs(fill = lgd, title=plot_title) +
                            #coord_flip() +
                            theme(legend.text=element_text(size=6))
         
      } else if(plot_type == "bar_stack"){
         plot <- data_tab %>% ggplot(aes(x = "", y = counts, 
                                  fill = labels)) +
                      geom_col(width = 1, color = 1) +
                      geom_label_repel(
                        aes(y = pos,
                            label = glue("{counts} ({percent(percentage)})"),
                             fill = labels),
                            show.legend = FALSE) +
                      labs(fill = lgd, title=plot_title) +
                      # coord_polar(theta = "y") +
                      theme_void() + 
                      theme(legend.text=element_text(size=6))
      }
        else if (plot_type == "bar_discrete") {
          plot <- data %>% ggplot(aes(y=counts, x=labels)) + 
                            geom_col(width = 0.7) +
                            labs(title=plot_title, 
                                 x=x_axis, y=y_axis) 
      } 
  }else if(var_type == "cont") {
        mu <- mean(df[,var_name], na.rm=TRUE)
        med <- median(df[,var_name], na.rm=TRUE) 
      if(plot_type == "hist") {
          
        plot <- ggplot(df, aes(x=.data[[var_name]])) + 
                      geom_histogram(fill = "#f79d27",
                                     col = 'black', bins=10) 
        
      }else if(plot_type == "boxplot") {
        plot <- ggplot(df, aes(x=.data[[var_name]])) + 
                geom_boxplot(outlier.colour="red",
                              outlier.size=2)
      }
        plot <- plot +
                geom_vline(xintercept = mu,
                           col="#228B22", lty=1, lwd = 1) +
                geom_vline(xintercept = med, 
                         col="#87CEEB", lty=2, lwd = 1) +
                theme_bw() +
                labs(title=plot_title, 
                     subtitle = paste("Mean = ", round(mu, 2), 
                                      "  Median = ", med), 
                     x=x_axis, y=y_axis) 
  }
  return(plot)
}

```

### General Comparison

```{r}
generic_compare <- function(data, var_type, var1, var2, 
                          var1_title, var2_title, 
                          subplot_type, plot_title,
                          lgd_title, x_axis=NULL, y_axis=NULL,
                          char_remove=NULL){
  var1_plot <- plot_func(data, var1, var_type, lgd = lgd_title,
                         var1_title, subplot_type, char_remove,
                         x_axis=x_axis, y_axis=y_axis)
  var2_plot <- plot_func(data, var2, var_type,lgd = lgd_title,
                          var2_title, subplot_type, char_remove,
                         x_axis=x_axis, y_axis=y_axis)
  if (subplot_type == "bar_simple" || subplot_type == "bar_stack") {
        plot <- ggarrange(var2_plot + remove_y, var1_plot + remove_y, 
                          ncol = 2,  nrow = 1, 
                          common.legend = TRUE,legend="bottom")
  } else {
        plot <- ggarrange(var2_plot, var1_plot, 
                        ncol = 2, nrow = 1, 
                        common.legend = TRUE,
                        legend="right")
  }
  
  return(annotate_figure(plot, top = text_grob(plot_title, 
                 color = "black", face = "bold", size = 12)))
}
```

### Comparison Unpaired Post-Pre

```{r}
compare_pre_post <- function(df_pre, df_post,
                             var_name, var_type, subplot_type, title=NULL, 
                             exclude_outliers = FALSE, lgd_title,
                             x_axis=NULL, y_axis=NULL,
                             char_remove=NULL, shared_legend=TRUE) {

  pre_plot <- plot_func(df_pre, var_name, var_type,
                         "Pre", subplot_type, lgd = lgd_title,
                        x_axis=x_axis, y_axis=y_axis,
                        char_remove=char_remove, 
                        remove_outliers=exclude_outliers)
  post_plot <- plot_func(df_post, var_name, var_type,
                          "Post", subplot_type, lgd = lgd_title,
                         x_axis=x_axis, y_axis=y_axis,
                         char_remove=char_remove, 
                         remove_outliers=exclude_outliers)
  if (subplot_type == "bar_stack") {
        plot <- ggarrange(post_plot + remove_y, pre_plot + remove_y, 
                          ncol = 2,  nrow = 1, 
                          common.legend = shared_legend,legend="bottom")
  }else if (subplot_type == "bar_simple") {
        plot <- ggarrange(post_plot, pre_plot + remove_y, 
                          ncol = 2,  nrow = 1, 
                          common.legend = shared_legend,legend="bottom")
  } else {
        plot <- ggarrange(post_plot, pre_plot, 
                          ncol = 2, nrow = 1, 
                          common.legend = shared_legend,
                          legend="right")
  }
      
  return(annotate_figure(plot, 
                         top = text_grob(title, color = "black", 
                                         face = "bold", size = 12)))

}
```

### Comparison Paired Post-Pre

```{r}
compare_paired <- function(data, var_name, view,
                           lgd_title, plot_title,
                          char_remove=NULL){
    var_pre <- as.factor(data[,paste(var_name, "pre", sep="_")])
    var_post <- as.factor(data[,paste(var_name, "post", sep="_")])
    labels_all <- c(unique(var_pre[is.na(var_pre) == FALSE]),
                    unique(var_post[is.na(var_post) == FALSE]))
  
    x <- list(labels = unique(labels_all))
    paired_df <- as.data.frame(x)
    counts_post <- as.data.frame(t(table(var_post)))[,2:3]
    props_post <- as.data.frame(prop.table(table(var_post)))
    setnames(counts_post,
             old = c('var_post','Freq'),
             new = c('labels','counts_post'))
    setnames(props_post,
             old = c('var_post','Freq'),
             new = c('labels','props_post'))
    
    counts_pre <- as.data.frame(t(table(var_pre)))[,2:3]
    props_pre <- as.data.frame(prop.table(table(var_pre)))
    setnames(counts_pre,
             old = c('var_pre','Freq'),
             new = c('labels','counts_pre'))
    setnames(props_pre,
         old = c('var_pre','Freq'),
         new = c('labels','props_pre'))
    
    df_list <- list(paired_df, counts_post, counts_pre, props_pre, props_post)
    merged <- df_list %>% reduce(left_join, by='labels')
    merged <- merged %>% replace(is.na(.), 0)
    merged$diff_counts <- merged$counts_post - merged$counts_pre
    merged$diff_props <- merged$props_post - merged$props_pre
    merged$count_change <- merged$diff_counts/merged$counts_pre
    print(merged)
    
    if(is.null(char_remove) == FALSE) {
      merged <- merged %>% filter(!.data[['labels']] %in% char_remove)
      }
    
    # side_plot <- 
    count_plot <- merged %>% ggplot(aes(x = labels, y = diff_counts)) +
                      geom_bar(aes(fill = labels), stat="identity") +
                      geom_label_repel(
                        aes(label = 
                              glue("{diff_counts} ({percent(count_change)})"),
                            fill = labels),
                            show.legend = FALSE) +
                      labs(fill = lgd_title, 
                           y="Difference in Counts") +
                        theme(legend.text=element_text(size=6)) + 
                        remove_x
    
    prop_plot <- merged %>% ggplot(aes(x = labels, y = diff_props)) +
                  geom_bar(aes(fill = labels), stat="identity") +
                  geom_label_repel(
                    aes(label = 
                          glue("{percent(diff_props)}"),
                        fill = labels),
                        show.legend = FALSE) +
                  labs(fill = lgd_title,  
                       y="Difference in Proportions") +
                    theme(legend.text=element_text(size=6)) + 
                    remove_x
    
    plot <- ggarrange(count_plot, prop_plot,
                          ncol = 2,  nrow = 1, 
                          common.legend = TRUE,legend="bottom")

    print(annotate_figure(plot, 
                         top = text_grob(plot_title, color = "black", 
                                         face = "bold", size = 12)))
}
```

### Violin Plots

```{r}
violins <- function(data, var_names, show_median, new_names, title=NULL){
  
  cols <- c("renewvia_id")
  for(var in var_names) {
    pre_name <- paste(var, "pre", sep="_")
    post_name <- paste(var, "post", sep="_")
    cols <- c(cols,pre_name, post_name)
  }
  
  test_paired <- data[, cols]
  # Split the data in two groups
  #test_paired <- outliers_removal(test_paired, pre_name)
  #test_paired <- outliers_removal(test_paired, post_name)
  test_paired_longer <- test_paired %>%
                                pivot_longer(
                                  cols = -renewvia_id,
                                  #names_to = "when",
                                  # names_prefix = var_name,
                                  # values_to = var_name,
                                  # values_drop_na = TRUE,
                                  # names_transform = list(var_name = as.numeric)
                                  names_to = c(".value","when"), 
                                  names_pattern =  "(\\w+)_(pre|post)"
                                )
  #test_paired_longer
  #var_norm <- paste(var_name, "normalized", sep="_")
  test_paired_longer[, var_names] <- normalize(test_paired_longer[, var_names])
  print(test_paired_longer)
  df_pre <- test_paired_longer %>% filter(when == "pre")
  df_post <- test_paired_longer %>% filter(when == "post")
  # Plot each side and join them
  
  vioplot(df_pre,
          #horizontal=TRUE, 
          wex=1.2,
          plotCentre = show_median, # Median with a line
          side = "left",     # Left side
          rectCol = NA, lineCol = NA,
          colMed="forestgreen", 
          h=0.25,
          names=new_names,
          main=title,
          ylab = "Normalized Value", 
          col = "#ef641e", ylim=c(0,1))        
  
  vioplot(df_post,
          #horizontal=TRUE,
          wex=1.2,
          plotCentre = show_median, # Median with a line
          side = "right",   # Right side
          col = "#87CEEB",
          ylim = c(0,1),
          colMed="forestgreen",
          h=0.25,
          rectCol = NA, lineCol = NA,
          add = TRUE)  # Color for the right side
  
  legend("topleft",
         legend = c("Pre", "Post"),
         fill = c("#ef641e", "#87CEEB"))
  
  # title(main=title, #xlab = "Variables", 
  #       ylab = "Normalized Value")
}
```

## Hypothesis Testing

```{r}
# Running the paired t-test
paired_testing <- function(data, var_name, test_type,
                           diff_type="magnitude",
                           plot_diff=FALSE, plt_title=NULL,
                           threshold=NULL,threshold_bound=NULL,
                           remove_outliers=FALSE, x_axis, y_axis) {
  pre_name <- paste(var_name, "pre", sep="_")
  post_name <- paste(var_name, "post", sep="_")
  #var_pre <- data[, pre_name]
  #var_post <- data[, post_name]
  
  if(diff_type == "direction"){
        data$var_diff <- ifelse(data[, post_name] > data[, pre_name], 1,
                               ifelse((data[, post_name] < data[, pre_name]), -1, 0))
      }else if(diff_type == "magnitude") {
        data$var_diff <- data[, post_name] - data[, pre_name]
      }
      
  data$diff_abs <- abs(data$var_diff)
  if(remove_outliers==TRUE) {
    data <- outliers_removal(data=data, var="diff_abs")
  }
  
  if(is.null(threshold) == FALSE) {
    if(threshold_bound == "lower"){
      data <- data %>% filter(diff_abs < threshold)
    }else if(threshold_bound == "upper"){
      data <- data %>% filter(diff_abs > threshold)
    }
  }

  # Running the test
  if(test_type == "wilcoxon"){
    #Wilcoxon Signed-Rank Test
    test <- wilcox.test(data[, pre_name], data[, post_name], paired=TRUE, 
                        conf.int = T, correct = T, exact = F, conf.level = .95)
  }else if(test_type == "sign") {
    #Sign Test
    test <- signtest(data$var_diff, m=0, conf.level=0.95, exact=FALSE)
  } else if (test_type == "ttest") {
    #Paired t-Test
    test <- t.test(data[, pre_name], data[, post_name],
         paired = TRUE, alternative = "two.sided")
  } else if(test_type == "mcnemar") {
    cross_tab <- table(data[, pre_name], data[, post_name])
    print(cross_tab)
    #test <- mcnemar.test(cross_tab) 
    test <- mcnemar.exact(cross_tab)
  }
  print(test)
  # Visualize distribution of score differences
  if(plot_diff == TRUE) {
      data$var_diff <- as.integer(data$var_diff)
      plot <- plot_func(df=data, var_name="var_diff", var_type="cont", 
                        plot_title=plt_title, plot_type="hist",
                        x_axis=x_axis, y_axis=y_axis)
      return(plot)
  }
  # return(test)
}
```

## Regression Analysis

### Plotting Scatter-plots

```{r}
plot_reg <- function(data, feature, dependent, 
                     remove_outliers=FALSE, which_outliers=NULL,
                     reg_type, vals_remove=NULL,title=NULL,
                     x_axis=NULL, y_axis=NULL, p_val=NULL, est=NULL, unit=NULL, extra=NULL) {
  
  if(is.null(vals_remove) == FALSE) {
    data <- data %>% filter(!.data[[dependent]] %in% vals_remove)
  }
  
  if(remove_outliers == TRUE) {
      if(which_outliers=="dependent"){
        data <- outliers_removal(data=data, var=dependent)
        
      }else if(which_outliers=="feature"){
        data <- outliers_removal(data=data, var=feature)
        
      }else if(which_outliers=="all"){
        temp <- outliers_removal(data=data, var=feature)
        data <- outliers_removal(data=data, var=dependent)
      }
  }
  

  if(reg_type == "linear") {
    plot <- ggplot(data,
                aes(x=.data[[feature]], y=.data[[dependent]])) +
                geom_point(color= "#ef641e") +
                  geom_smooth(color="#87CEEB", method = "lm", se = FALSE) 
    
  } else if(reg_type == "logistic") {
    
     plot <- ggplot(data, 
                    aes(x=.data[[feature]], y=.data[[dependent]])) + 
              geom_jitter(width = 0.05, height = 0.05, color= "#ef641e") +
              #geom_point(color='blue', alpha=.5) +
             geom_smooth(method = "glm", color="#87CEEB",
                         method.args= list(binomial(link = 'logit')), se=FALSE)
                
  }else if(reg_type == "poisson") {
     plot <- ggplot(data, 
                    aes(x=.data[[feature]], y=.data[[dependent]])) + 
              #geom_point(color='blue', alpha=.5) +
              geom_jitter(width = 0.05, height = 0.05) +
              geom_smooth(method = "glm", color="#87CEEB",
                         method.args= list(family="poisson"), se=TRUE)
                
  }
  if (typeof(p_val) == "character"){
    plot <- plot +
          labs(subtitle = TeX(sprintf(r"($Slope = %.3f\ %s\ %s,
                                      \textit{p} = %s$)", est, unit,extra, p_val)),
                      y=y_axis, x=x_axis)  +
   theme_classic() +
    theme( axis.title = element_text(size=13),
           axis.text=element_text(size=13),
           plot.subtitle=element_text(size=13))
  }else {
    plot <- plot +
          labs(subtitle = TeX(sprintf(r"($Slope = %.3f\ %s\ %s,
                                      \textit{p} = %.3f$)", est,  unit,extra,  p_val)),
                      y=y_axis, x=x_axis)  +
    theme_classic() +
    theme( axis.title = element_text(size=13),
           axis.text=element_text(size=13),
           plot.subtitle=element_text(size=13))
  }
  
  return(plot)
}
```

### Regression - Community

```{r}
ind_vars <- c("PV_Size_kWp",	"Customers",	"CAPEX_USD")
axes_names <- c("PV Size [kWp]",	"No. of Customers",	"CAPEX [K USD]")
extract_p_reg <- function (modelobject) {
   if (class(modelobject) != "lm") {
     stop("Not an object of class 'lm' ")
     
   }else {
       f <- summary(modelobject)$fstatistic
       p <- pf(f[1],f[2],f[3],lower.tail=F)
       attributes(p) <- NULL
       return(p)
     }
   
}
community_reg <- function(df, col_name, 
                          dep, 
                          customer_type,
                          var_type, 
                          title=NULL, 
                          unit_val = NULL, extra=NULL, 
                          sig_var=NULL,
                          calc_diff=FALSE, diff_type=NULL,
                          to_remove=NULL, exclude_outliers = FALSE, 
                          outliers=NULL, y_axis=NULL) {
  if (calc_diff == TRUE) {
      pre_name <- paste(col_name, "pre", sep="_")
      post_name <- paste(col_name, "post", sep="_")
      if(diff_type == "direction"){
        df$col_reg <- ifelse(df[, post_name] > df[, pre_name], 1,
                               ifelse((df[, post_name] < df[, pre_name]), -1, 0))
      }else if(diff_type == "magnitude") {
        df$col_reg <- df[, post_name] - df[, pre_name]
      }
      
      names(df)[names(df) == "community_post"] <- "community"
      
  } else {
      df$col_reg <- df[, col_name]
  }
  
  if(var_type == "categorical") {
    data <- rownames_to_column(as.data.frame.matrix(
                                  prop.table(table(
                                      df[, "community"], 
                                      df[, "col_reg"]),
                                     margin = 1)), 
                               var = "community")
    community_data <- merge(x=projects, y=data, by="community")
    community_data$target <- as.integer(community_data[, dep]*community_data[, customer_type])
  } else if(var_type == "ratio") {
    data <- as.data.frame(rowsum(df[, "col_reg"], 
                                 df[, "community"], na.rm = TRUE))
    data$community <- rownames(data)
    community_data <- merge(x=projects, y=data, by="community")
    names(community_data)[names(community_data) == "V1"] <- "target"
  }
  
  
  if(is.null(to_remove) == FALSE) {
    #community_data <- community_data[!grepl(to_remove,data$target),]
    community_data <- community_data %>% filter(!.data[["target"]] %in% to_remove)
  }
  

  print(community_data)
  target_dist_data <- outliers_removal(data=community_data, var="target")
  dist <- plot_func(df=target_dist_data, var_name="target", var_type="cont", 
                    plot_title="Dependent Variable Boxplot", plot_type="boxplot", 
                    char_remove=NULL,
                    remove_outliers = FALSE,
                    x_axis=NULL, y_axis=NULL)
  
  lst <- list(dist)
  lst_sig <- list()  
  for(i in seq_along(ind_vars)) {
     ind <- ind_vars[i]
     print(ind)
     
     if(exclude_outliers == TRUE) {
          community_data <- outliers_removal(data=community_data, var=ind)
     }
      lm <- lm(community_data[,"target"] ~ community_data[,ind])
      details <- summary(lm)
      p_value <- summary(lm)$coefficients["community_data[, ind]", "Pr(>|t|)"]
      estimate <- summary(lm)$coefficients["community_data[, ind]", "Estimate"]
      print(estimate)
      print(p_value)
      print(confint(lm, level=0.95))
      if (sig_var == "CAPEX_USD"){
        estimate <- estimate * 1000
        print(estimate)
      }
      # else if(sig_var == "Customers"){
      #   estimate <- estimate * 100
      # } else {
      #   estimate <- estimate * 10
      # }
      
      if (col_name == "better_access_health_minigrid" | col_name == "minigrid_access_life_improvement"){
        p_value_sci <- formatC(p_value, format = "e", digits = 2)
        print(typeof(p_value_sci))
        plt <- plot_reg(data=community_data, feature=ind,
              dependent="target", reg_type="linear",
              # remove_outliers = exclude_outliers,
              # which_outliers = outliers,
              unit = unit_val,
              extra=extra,
              est = estimate,
              p_val = p_value_sci,
              x_axis = axes_names[i],
              y_axis=y_axis)
      } else {
        plt <- plot_reg(data=community_data, feature=ind,
              dependent="target", reg_type="linear",
              # remove_outliers = exclude_outliers,
              # which_outliers = outliers,
              unit = unit_val,
              extra=extra,
              est = estimate,
              p_val = p_value,
              x_axis = axes_names[i],
              y_axis=y_axis)
      }
      lst <- append(lst, list(plt))
      pearson_test <- cor.test(community_data[, "target"], 
                               community_data[,ind], 
                               method="pearson")
      print(pearson_test)
      if(p_value < 0.05 & ind == sig_var) {
        if (sig_var == "CAPEX_USD"){
          plt <- plt + scale_x_continuous(labels =
                                            label_number(
                                              #suffix = "K",
                                                         scale = 1e-3))
        }
        lst_sig <- append(lst_sig, list(plt))
      }

    }
  plot <- ggarrange(plotlist = lst,
                    ncol = 2, nrow = 2,
                    common.legend = TRUE,
                    legend="right")
  annotate_figure(plot, top = text_grob(title,
                 color = "black", face = "bold", size = 12))

  vars_sig <- length(lst_sig)
  print(vars_sig)
  if (vars_sig > 0) {
      sig_plots <- ggarrange(plotlist = lst_sig,
                    ncol = 1, nrow = vars_sig,
                    font.label=list(color="black",size=12))
      ggsave(paste(col_name, "_regression_community.pdf"), sig_plots,
                   width = 4, height = 4, dpi = 400, device='pdf')
      sig_plots
  }

  }
```

### Regression - Individual

```{r}
consumption_reg <- function(df, dep, ind, title, reg_type, 
                            calc_diff=FALSE, diff_type=NULL,
                            exclude_outliers = FALSE,
                            outliers=NULL, to_remove=NULL,
                            x_axis=NULL, y_axis=NULL,
                            normalize=FALSE, 
                            threshold=NULL, 
                            threshold_bound=NULL,
                            log_direction=NULL) {

  if (calc_diff == TRUE) {
      pre_name <- paste(dep, "pre", sep="_")
      post_name <- paste(dep, "post", sep="_")
      if(diff_type == "direction"){
        df$col_reg <- ifelse(df[, post_name] > df[, pre_name], 1,
                               ifelse((df[, post_name] < df[, pre_name]), -1, 0))
      }else if(diff_type == "magnitude") {
        df$col_reg <- df[, post_name] - df[, pre_name]
      }
      
    } else {
      df$col_reg <- df[, dep]
    }
  
  if(is.null(threshold) == FALSE) {
    if(threshold_bound == "lower"){
      df <- df %>% filter(col_reg < threshold)
    }else if(threshold_bound == "higher"){
      df <- df %>% filter(col_reg > threshold)
    }
  }
      
  if(normalize==TRUE) {
    df$col_reg <- normalize(df$col_reg)
  }
  print(dim(df))
  print(head(df[, c(ind, "col_reg")]))
  
  if(reg_type == "linear") {
    model <- lm(df$col_reg ~ df[, ind])
    print(summary(model))
    print(confint(model, level=0.95))
    p <- plot_reg(data=df, feature=ind,  
                  dependent="col_reg", reg_type="linear", 
                  remove_outliers=exclude_outliers, 
                  which_outliers = outliers,
                  vals_remove=to_remove,
                  title=title, x_axi=x_axis, y_axis=y_axis)
    test <- cor.test(df$col_reg, df[, ind], 
                     method="pearson")
    print(test)
    
  } else if(reg_type == "logistic") {
    #if(calc_diff == TRUE) {
    if(log_direction == 1) {
      df <- df %>% filter(col_reg >= 0)
    }else if(log_direction == -1) {
      df <- df %>% filter(col_reg <= 0)
      df$col_reg <- ifelse(df$col_reg == -1, 1, 0)
    }
    model <- glm(df$col_reg ~ df[, ind], 
               family="binomial")
    print(summary(model))
    print(confint(model, level=0.95))
    test <- anova(model,test=c("LR"))
    print(test)
    p <- plot_reg(data=df, feature=ind,  
                  dependent="col_reg", reg_type="logistic", 
                  remove_outliers=exclude_outliers,
                  which_outliers = outliers,
                  vals_remove=to_remove,
                  title=title, x_axi=x_axis, y_axis=y_axis)
    #test <- wald.test(Sigma = vcov(model), b = coef(model), Terms = 1)
    
  }else if(reg_type == "poisson") {
    model <- glm(df$col_reg ~ df[, ind], 
               family="poisson")
    print(summary(model))
    print(confint(model, level=0.95))
    p <- plot_reg(data=df, feature=ind,  
                  dependent="col_reg", reg_type="poisson", 
                  remove_outliers=exclude_outliers,
                  which_outliers = outliers,
                  vals_remove=to_remove,
                  title=title, x_axi=x_axis, y_axis=y_axis)
    #test <- wald.test(Sigma = vcov(model), b = coef(model), Terms = 1)
    print(test)
  }
  return(p)
  
}
```

```{r}
# rg <- preProcess(as.data.frame(paired_enc$kerosene_lamps_count_post), 
#                    method=c("range"))
#  
# temp <- predict(rg, as.data.frame(paired_enc$kerosene_lamps_count_post))
# temp$consumption <- paired_enc$avg_mon_consumption_period
# paired_enc$test <- log(paired_enc$water_cost_post)
# ggplot(paired_enc,
#         aes(x=avg_mon_consumption_period, 
#             y=test)) +
#         geom_point(color='blue') +
#           geom_smooth(color='red', method = "lm", se = TRUE) +
#         theme_classic()
```

# 1- General

## A) Question

```{r, fig.width=6, fig.height=6}
q_dist <- read.csv("q_dist_per.csv")
q_dist$per <- round(q_dist$per * 100)
survey_names <- c(
                    `hs_pre` = "Household \nPre-Survey",
                    `hs_post` = "Household \nPost-Survey",
                    `ci_post` = "Commercial & \n Institution Post-Survey"
                    )
q_plot <- q_dist %>% ggplot(aes(y=per, x=Axis, fill=Axis)) +
                              geom_col(width = 0.5) +
                              ylim(0, 50) + 
                              guides(fill=guide_legend(nrow=2,byrow=TRUE)) + 
                              geom_label_repel(
                                aes(label = glue("({per}%)"),
                                     fill = Axis),
                                hjust=0.75,nudge_y = 0.75,direction="y",
                                    show.legend = FALSE) +
                              labs(fill = "Survey", y="Percent of Questions (%)"
                                   #title="Distribution of Survey Questions"
                                   )+ 
                              #coord_flip() +
                              facet_grid(
                                         ~factor(survey,
                                                 levels=c("hs_pre", "hs_post",
                                                          "ci_post")),
                                         labeller = as_labeller(survey_names),
                                         switch = "both") 
                              #theme(legend.text=element_text(size=6))
q_plot <- q_plot + theme_classic() +
    #scale_fill_manual() +
    scale_fill_manual(name = "", values=c("#ef641e","#f79d27", 
                               "#228B22", "#b2713d", "#87CEEB")) +
                        theme(legend.position = 'top', 
                       legend.text=element_text(size=12),
                       strip.background = element_blank(),
                       strip.text = element_text(size = 12),
                       axis.text=element_text(size=12),
                       axis.title=element_text(size=12),
                       strip.placement = "outside") +
                        remove_x 


q_plot <- q_plot + draw_line(
                    x = c(0),
                    y = c(0, 50),
                    color = "grey", size = .5
                                )

q_plot
ggsave("questions_distribution_plot.pdf", q_plot)
```

## A) Gender

```{r, fig.width=6, fig.height=6}
## What was the gender breakdown of survey respondents, pre and post?
# Unpaired

g_dist <- read.csv("gender_dist_per.csv")
g_dist$per <- round(g_dist$per * 100)
survey_names <- c(
                    `hs_pre` = "Household \nPre-Survey",
                    `hs_post` = "Household \nPost-Survey"
                    )
g_plot <- g_dist %>% ggplot(aes(y=per, x=Gender, fill=Gender)) +
                              geom_col(width = 0.8) +
                              ylim(0, 100) +
                              geom_label_repel(
                                aes(label = glue("({per}%)"),
                                     fill = Gender),
                              hjust=0.75,nudge_y = 0.75,direction="y",
                                    show.legend = FALSE) +
                              labs(y="Percent of Respondents (%)"
                                   #title="Distribution of Survey Questions"
                                   )+ 
                              #coord_flip() +
                              facet_grid(
                                         ~factor(survey,
                                                 levels=c("hs_pre", "hs_post")),
                                         labeller = as_labeller(survey_names),
                                         switch = "both") 
                              #theme(legend.text=element_text(size=6))
g_plot <- g_plot + theme_classic() +
    #scale_fill_manual() +
    scale_fill_manual(name="", values=c("#ef641e", "#87CEEB" 
                               #"#228B22", "#b2713d", "#87CEEB"
                               )) +
                        theme(legend.position = 'top', 
                       legend.text=element_text(size=12),
                       strip.background = element_blank(),
                       strip.text = element_text(size = 12),
                       axis.text=element_text(size=12),
                       axis.title=element_text(size=12),
                       strip.placement = "outside") +
                        remove_x 

g_plot <- g_plot + draw_line(
                    x = c(0),
                    y = c(0, 100),
                    color = "grey", size = .5
                                )

ggsave("gender_distribution_plot.pdf", g_plot)
g_plot
```

## B) Age

```{r}
age_plot <- compare_pre_post(df_pre=initial_pre, df_post=post_clean,
                 var_name="age", var_type="cont",
                 subplot_type="hist", shared_legend=FALSE,
                 exclude_outliers = TRUE,
                 x_axis="Age", y_axis="Count",
                 #title="Age Distrbution"
                 )

# Paired
# plot_func(df=paired_clean, 
#           var_name="age_post", 
#           var_type="cont", lgd = "Gender",
#           plot_title="Paired: Age", 
#           remove_outliers = TRUE,
#           plot_type="hist")
#age_plot
#ggsave("age_plot.pdf", age_plot)
```

## C) Household Size

```{r}
# Type of employment for Primary Provider
plot_func(df=initial_pre, var_name="household_headcount",
          var_type="cont", lgd = "Gender",
          plot_title="Headcount", 
          remove_outliers = TRUE,
          plot_type="hist")
```

## D) Employment Type

```{r}
# Type of employment for Primary Provider
plot_func(df=initial_pre, var_name="employement_type", 
          var_type="non_cont", lgd="Type",
          plot_title="Employement Type of Primary Provider", 
          plot_type="pie")
```

## E) Correlation - Dependent Variables

```{r}
corr_simple <- function(data,sig=0){
  #convert data to numeric in order to run correlations
  #convert to factor first to keep the integrity of the data - each value will become a number rather than turn into NA
  data <- data[, !names(data) %in% c("renewvia_id","X", 
                                     "end", "end_date", "displayName",
                                     "meterSerial", "projectName",
                                     "Sum.of.kWh.Consumed.y",
                                     "avg_mon_consumption_cum")]
  #df_cor <- data %>% mutate_if(is.character, as.factor)
  # df_cor <- df_cor %>% mutate_if(is.factor, as.numeric)
  df_cor <- data %>% keep(is.numeric)
  #run a correlation and drop the insignificant ones
  #corr <- cor(df_cor)
  #corr <- rcorr(as.matrix(df_cor))
  #prepare to drop duplicates and correlations of 1     
  # corr[lower.tri(corr,diag=TRUE)] <- NA 
  # #drop perfect correlations
  #corr[corr == 1] <- NA 
  #turn into a 3-column table
  #corr <- as.data.frame(corr)
  #remove the NA values from above 
  # corr <- na.omit(corr) 
  #select significant values  
  # corr <- subset(corr, abs(Freq) > sig) 
  # #sort by highest correlation
  # corr <- corr[order(-abs(corr$Freq)),] 
  #print table
  return(corrplot(cor(df_cor), method="number", tl.pos='n'))
  # #turn corr back into matrix in order to plot with corrplot
  # mtx_corr <- reshape2::acast(corr, Var1~Var2, value.var="Freq")
  # #plot correlations visually
  # corrplot(mtx_corr, is.corr=FALSE, tl.col="black", na.label=" ")
}
```

```{r, fig.width=16, fig.height=16}
vars_pre_cor <- c(
  'age', 'avg_household_income', 'household_headcount',
  'adult_headcount', 'girls_headcount', 'boys_headcount', 
  'appliances_count', 'cellphones_count', 'light_hours_current',
  'kerosene_lamps_count',
  'kerosene_lamp_usage_time', 'kerosene_lamps_cost', 
  'cooking_fuel_collection_time', 
  'cooking_energy_cost', 
  'applicances_charging_cost', 'phone_charge_frequency',
  'phone_charge_cost', 'phone_charge_travel_distance', 'water_collection_travel_distance',
  'water_collection_time', 
  'avg_person_age_water_collection', 'water_cost',
  'clinic_travel_distance'
)
df_cor <- initial_enc %>% keep(is.numeric)
pre_cor <- initial_enc[, vars_pre_cor]

pdf("hs_pre_corr_plot.pdf")
corrplot(res_pre$r, type="lower", order="hclust", 
         p.mat = res_pre$P, sig.level = 0.05, 
         #tl.cex = 2.0, 
         tl.col="#b2713d",
         col = colorRampPalette(c("#ef641e","#f79d27","#228B22"))(10), insig = "blank")
dev.off()
# ggsave(, pre_cor_plot)
```

```{r, fig.width=16, fig.height=16}
# HS Post-survey
vars_post_cor <- c(
'age',
'avg_household_income',
'appliances_count', 'cellphones_count',
'light_hours_current', 
'kerosene_lamps_count',
'kerosene_lamps_cost', 
'cooking_fuel_collection_time',
'cooking_energy_cost', 
'applicances_charging_cost', 
'phone_charge_frequency', 'phone_charge_cost',
'phone_charge_travel_distance', 
'water_collection_travel_distance', 'water_collection_time',
'water_cost', 'clinic_travel_distance'
)
#df_cor <- post_enc %>% keep(is.numeric)
post_cor <- post_enc[, vars_post_cor]
res_post <- rcorr(as.matrix(post_cor))

pdf("hs_post_corr_plot.pdf")
corrplot(res_post$r, type="lower", order="hclust", 
         p.mat = res_post$P, sig.level = 0.05, 
         #tl.cex = 2.0, 
         tl.col="#b2713d",
         col = colorRampPalette(c("#ef641e","#f79d27","#228B22"))(10), insig = "blank")
dev.off()
```

```{r, fig.width=8, fig.height=8}
# C&I Post-survey
# HS Post-survey
vars_post_cor <- c(
'business_hours_increase',
 'appliances_addition_count',
 'health_offering_change_count'
)

post_cor <- ci_enc[, vars_post_cor]
res_post <- rcorr(as.matrix(post_cor))

pdf("ci_post_corr_plot.pdf")
corrplot(res_post$r, type="lower", order="hclust", 
         p.mat = res_post$P, sig.level = 0.05, 
         #tl.cex = 1.0, 
         tl.col="#b2713d",
         col = colorRampPalette(c("#ef641e","#f79d27","#228B22"))(10), insig = "blank")
dev.off()
```

```{r}
# computing p values of the data loaded
# p_values <- rcorr(as.matrix(initial_enc))
# print(p_values)
#corrplot(initial_enc, method="number")
```

# 2- Gender Equality

## A) Descriptive

### Pre-Connection School Enrollment

```{r}
# What was school enrollment by gender pre-connection?
girls <- sum(initial_pre$girls_headcount,na.rm = TRUE)
girls_in_school <- sum(initial_pre$girls_schooling,na.rm = TRUE)
enrollment_rate <- percent(girls_in_school/girls, accuracy = 0.01)

vals <- c(girls, girls_in_school, enrollment_rate)

# creating matrix
tab <- as.data.frame(t(as.matrix(vals)))
setnames(tab, old = c('V1','V2', 'V3'), 
          new = c("Girls", "Girls.In.School", "Enrollment.Rate"))
```

```{r}
# What was school enrollment by gender pre-connection?
boys <- sum(initial_pre$boys_headcount,na.rm = TRUE)
boys_in_school <- sum(initial_pre$boys_schooling,na.rm = TRUE)
enrollment_rate <- percent(boys_in_school/boys, accuracy = 0.01)

vals <- c(boys, boys_in_school, enrollment_rate)

# creating matrix
tab <- as.data.frame(t(as.matrix(vals)))
setnames(tab, old = c('V1','V2', 'V3'),
          new = c("Boys", "Boys.In.School", "Enrollment.Rate"))
tab
```

### School Enrollment Change

```{r}
# Was there a change in enrollment by gender afterwards?
# Unpaired
generic_compare(data=post_clean, var_type="non_cont",
               var1="girls_schooling_change", 
               var2="boys_schooling_change", 
               lgd_title ="Change",
               var1_title="Girls", var2_title="Boys", 
               subplot_type="bar_stack", plot_title="Post: School Enrollment Change")

# Paired
generic_compare(data=paired_clean, var_type="non_cont",
               var1="girls_schooling_change", 
               var2="boys_schooling_change", 
               lgd_title ="Change",
               var1_title="Girls", var2_title="Boys", 
               subplot_type="bar_stack", 
               plot_title="Paired: School Enrollment Change")
```

### Reasons for (un)enrollment

#### TODO: Girls' Schooling

```{r}
# Dirving factor for non-enrollment in school for boys and girls
# Unpaired
compare_pre_post(df_pre=initial_pre, df_post=post_clean,
                 var_name="girls_unschooled_reasons", 
                 var_type="non_cont",
                 lgd_title ="Reasons",
                 subplot_type="bar_stack",
                 char_remove = c("they_all_attend_school", 
                 "they_all_attend_school_full_time"),
                 title="Unpaired - Girls Schooling: Reasons for non-enrollment")

# For Girls
compare_paired(data=paired_clean,
               var_name="girls_unschooled_reasons",
               lgd_title="Reasons",
               char_remove = c("they_all_attend_school", 
                 "they_all_attend_school_full_time"),
               plot_title="Girls Schooling: Reasons for non-enrollment")
```

#### Boys' Schooling

```{r}
# For Boys
# Unpaired
compare_pre_post(df_pre=initial_pre, df_post=post_clean,
                 var_name="boys_unschooled_reasons", 
                 var_type="non_cont",lgd_title ="Reasons",
                 subplot_type="bar_simple", 
                 char_remove = c("they_all_attend_school", 
                 "they_all_attend_school_full_time"),
                 title="Unpaired - Boys Schooling: Reasons for non-enrollment")

# Paired
compare_paired(data=paired_clean,
               var_name="boys_unschooled_reasons",
               lgd_title="Reasons",
               char_remove = c("they_all_attend_school", 
                 "they_all_attend_school_full_time"),
               plot_title="Paired - Boys Schooling: Reasons for non-enrollment")
```

### Household Chores

#### Water Collection - Responsibility

```{r}
# What is the average age of the person in charge of water collection?
# Unpaired
compare_pre_post(df_pre=initial_pre, df_post=post_clean,
                 var_name="avg_person_age_water_collection", 
                 var_type="non_cont",
                 lgd_title="Age Group",
                 subplot_type="bar_simple", 
                 title="Unpaired: Age of Person Responsible 
                 for Water Collection")

# Paired
compare_paired(data=paired_clean,
               var_name="avg_person_age_water_collection",
               lgd_title="Age Group",
               plot_title="Paired: Age of Person Responsible 
               for Water Collection")
```

#### Is the person responsible school-aged?

```{r}
# What is the average age of the person in charge of water collection? Binarized as school-aged vs not
# Unpaired
compare_pre_post(df_pre=initial_pre, df_post=post_clean,
                 var_name="water_collection_school_aged", 
                 var_type="non_cont", subplot_type="pie",
                 lgd_title="School-Aged?",
                 title="Unpaired: Water Collection Responsibility (School-Aged)")

# Paired
generic_compare(data=paired_clean, var_type="non_cont",
               var1="water_collection_school_aged_pre", 
               var2="water_collection_school_aged_post", 
               lgd_title ="School-Aged?",
               var1_title="Pre", var2_title="Post", 
               subplot_type="pie", 
               plot_title="Paired: Breakdown of Water Collection Responsibility (School-Aged)")

# Paired
compare_paired(data=paired_clean,
               var_name="water_collection_school_aged",
               lgd_title="School-Aged?",
               plot_title="Paired: Change of Water Collection Responsibility (School-Aged)")
```

#### Cooking Fuel Collection - Are men involved?

```{r}
# Who is mainly responsible for cooking fuel collection on a daily basis? Binarized as presence of "adult_male" vs not
# Unpaired
compare_pre_post(df_pre=initial_pre, df_post=post_clean,
                 var_name="cooking_fuel_responsible_binary", 
                 var_type="non_cont",
                 subplot_type="pie",
                 lgd_title="Are men involved?",
                 title="Unpaired: Shcool-Aged Person responsible 
                 for Cooking Fuel Collection")

# Paired
compare_paired(data=paired_clean,
               var_name="cooking_fuel_responsible_binary",
               lgd_title="Are men involved?",
               plot_title="Paired: Shcool-Aged Person responsible 
                 for Cooking Fuel Collection")
```

### Female Businesses Ownership - Subgroup by country, community

```{r}
# How many new women-led businesses were created?
# Unpaired
compare_pre_post(df_pre=initial_pre, df_post=post_clean,
                 var_name="business_owners_female", 
                 var_type="non_cont", 
                 lgd_title = "Is there a woman business owner?",
                  subplot_type="pie", 
                  title="Unpaired - Women Business Owners")

# Paired
compare_paired(data=paired_clean,
               var_name="business_owners_female",
               lgd_title="Is there a woman business owner?",
               plot_title="Paired: Women Business Owners")
```

#### Subgroup Analysis - Country

```{r}
ctr <- "nigeria"
country_pre <- initial_pre %>% filter(country == ctr)
country_post <- post_clean %>% filter(country == ctr)
compare_pre_post(df_pre=country_pre, df_post=country_post,
                 var_name="business_owners_female", 
                 var_type="non_cont", 
                 lgd_title = "Is there a woman business owner?",
                  subplot_type="bar_simple", 
                  title="Nigeria Unpaired: Women Business Owners")

# Paired
country_paired <- paired_clean %>% filter(country_post == ctr)
compare_paired(data=country_paired,
               var_name="business_owners_female",
               lgd_title="Is there a woman business owner?",
               plot_title="Nigeria Paired: Women Business Owners")
```

```{r}
ctr <- "kenya"
country_pre <- initial_pre %>% filter(country == ctr)
country_post <- post_clean %>% filter(country == ctr)
compare_pre_post(df_pre=country_pre, df_post=country_post,
                 var_name="business_owners_female", 
                 var_type="non_cont", 
                 lgd_title = "Is there a woman business owner?",
                  subplot_type="bar_simple", 
                  title="Kenya Unpaired: Women Business Owners")

# Paired
country_paired <- paired_clean %>% filter(country_post == ctr)
compare_paired(data=country_paired,
               var_name="business_owners_female",
               lgd_title="Is there a woman business owner?",
               plot_title="Kenya Paired: Women Business Owners")
```

#### Subgroup Analysis - Gender

```{r}
gdr <- "male"
gender_pre <- initial_pre %>% filter(gender == gdr)
gender_post <- post_clean %>% filter(gender == gdr)
compare_pre_post(df_pre=gender_pre, df_post=gender_post,
                 var_name="business_owners_female", 
                 var_type="non_cont", 
                 lgd_title = "Is there a woman business owner?",
                  subplot_type="bar_simple", 
                  title="Men Unpaired: Women Business Owners")

# Paired
gender_paired <- paired_clean %>% filter(gender_post == gdr)
compare_paired(data=gender_paired,
               var_name="business_owners_female",
               lgd_title="Is there a woman business owner?",
               plot_title="Men Paired: Women Business Owners")
```

```{r}
gdr <- "female"
gender_pre <- initial_pre %>% filter(gender == gdr)
gender_post <- post_clean %>% filter(gender == gdr)
compare_pre_post(df_pre=gender_pre, df_post=gender_post,
                 var_name="business_owners_female", 
                 var_type="non_cont", 
                 lgd_title = "Is there a woman business owner?",
                  subplot_type="bar_simple", 
                  title="Women Unpaired: Women Business Owners")

# Paired
gender_paired <- paired_clean %>% filter(gender_post == gdr)
compare_paired(data=gender_paired,
               var_name="business_owners_female",
               lgd_title="Is there a woman business owner?",
               plot_title="Women Paired: Women Business Owners")
```

### New Female Workers

```{r}
ci_enc$hired_women <- ifelse(ci_enc$workforce_change_female > 0, 1, 0)
plot_func(df=ci_enc, var_name="hired_women", 
          var_type="non_cont", lgd="Change",
          plot_title="Hiring Women Employees", 
          plot_type="bar_simple")
```

### TODO

-   Bar charts by groups, Chi-Square goodness of fit, proportions not counts

-   Qualitative Methods: In respondent's own words, how were women affected from the mini-grid?

## B) Inferential

### School Enrollment Change

**Data Source**: Household Post-Survey

**Value (Encoding if applied)**: "Yes, it's decreased" = -1; "No, it's the same" = 0; "Yes, it's increased" = 1

#### Regression - Community (Girls)\*

```{r, fig.width=6, fig.height=6}
## Has there been a change in the number of females in your household who attend school full time since connection to minigrid power?
# Check for increase
community_reg(df=post_enc,
              col_name="girls_schooling_change", dep="1", 
              var_type="categorical", customer_type="hs",
              exclude_outliers = TRUE, outliers = "feature",
              y_axis= "Households \nReporting Improvement",
              #title="Increase in Girls' School Enrollment by Community",
              sig_var="CAPEX_USD", unit_val = "HH/K", extra="USD"
              #title_sig="Increase of Girls Schooling in Communities"
              )
```

#### TODO: Investigate, RESOLVED

```{r}
# Check for decrease
community_reg(df=post_enc,
              col_name="girls_schooling_change", dep="-1", 
              var_type="categorical", customer_type="hs",
              exclude_outliers = TRUE, outliers = "feature",
              y_axis= "Households",
              title="Decrease in Girls' School Enrollment by Community")
```

#### Logistic Regression - Individual

```{r}
consumption_reg(df = post_enc, reg_type ="logistic",
                dep= "girls_schooling_change", 
                ind="avg_mon_consumption_cum",
                calc_diff=FALSE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption Cumulative (kwH)", 
                y_axis="Change", log_direction = 1,
                exclude_outliers = TRUE, outliers = "feature",
                title="Increase in Girls' School Enrollment vs Consumption")
```

#### Regression - Community (Boys)\*

```{r}
## Has there been a change in the number of males in your household who attend school FULL TIME since connection to minigrid power?
# Check for increase
community_reg(df=post_enc,
              col_name="boys_schooling_change", dep="1", 
              var_type="categorical", 
              exclude_outliers = TRUE, outliers = "feature",
              customer_type="hs", y_axis= "Households \nReporting Improvement",
              sig_var="CAPEX_USD", unit_val = "HH/K", extra="USD"
              #title_sig="Increase of Boys Schooling in Communities"
              )
```

```{r}
# Check for decrease
community_reg(df=post_enc,
              col_name="boys_schooling_change", dep="-1", 
              var_type="categorical", exclude_outliers = TRUE, 
              outliers = "feature",
              customer_type="hs", y_axis= "Households",
              title="Decrease in Boys' School Enrollment by Community")
```

#### Logistic Regression - Individual

```{r}
consumption_reg(df = post_enc, reg_type ="logistic",
                dep= "boys_schooling_change", ind="avg_mon_consumption_period",
                calc_diff=FALSE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption Pre-Post Period (kwH)", 
                y_axis="Water Collection Time", log_direction = 1,
                exclude_outliers = TRUE, outliers = "feature",
                title="Increase in Boys' School Enrollment vs Consumption")
```

### Water Collection Time

**Data Source**: Paired Household Surveys (Pre & Post)

**Value (Encoding if applied)**: "less than 1 hour" = 1; "1-2 hours" = 2; "2-3 hours" = 3; "3-4 hours" = 4; "greater than 4 hours" = 5

#### Paired Test\*

```{r}
# How long does the water collection process take on a daily basis?
paired_testing(paired_enc, var_name="water_collection_time", 
               test_type = "ttest", plot_diff=TRUE, 
               x_axis="Differences", y_axis="Count",
               remove_outliers = TRUE,
               plt_title="Difference in Pre-Post of Water Collection Time")
```

#### Linear Regression - Community\*

```{r}
## Community Paired Differences
# Directional 
community_reg(df=paired_enc, 
              col_name="water_collection_time", dep="-1", 
              var_type="categorical", 
              calc_diff = TRUE, diff_type = "direction",
              exclude_outliers = TRUE, outliers = "feature",
              customer_type="hs", y_axis= "Households Reporting\n Decrease",
              sig_var="CAPEX_USD", unit_val = "HH/K", extra="USD"
              #,title_sig="Decrease of Water Collection Time in Communities"
              )
```

```{r}
# Magnitude 
community_reg(df=paired_enc, 
              col_name="water_collection_time", dep="target", 
              var_type="ratio", 
              calc_diff = TRUE, diff_type = "magnitude",
              exclude_outliers = TRUE, outliers = "feature",
              customer_type="hs", y_axis= "Sum of Differences",
              title="Decrease (Magnitude) in Water Collection Time by Community")
```

#### Linear Regression - Individual

```{r}
## Paired Individual Directional Change
consumption_reg(df = paired_enc, reg_type ="linear",
                dep= "water_collection_time", ind="avg_mon_consumption_period",
                calc_diff=TRUE, diff_type = "magnitude",
                x_axis="Avg. Monthly Energy Consumption Pre-Post Period (kwH)", 
                y_axis="Water Collection Time", 
                normalize = TRUE,
                #threshold = 4, threshold_bound = "lower",
                title="Individual Directional Change vs Consumption")
```

#### TODO: Logistic Regression - Individual

```{r}
# Undesired Effect
consumption_reg(df = paired_enc, reg_type ="logistic",
                dep= "water_collection_time", 
                ind="avg_mon_consumption_period",
                calc_diff=TRUE, diff_type = "direction",
                x_axis="Avg. Monthly Consumption Pre-Post Period (kwH)", 
                y_axis="Change (Decrease)", log_direction = -1,
                exclude_outliers = TRUE, outliers = "feature",
                title="Water Collection Time Change vs Consumption")
```

### Water Collection School-Aged

**Data Source**: Paired Household Surveys (Pre & Post)

**Value (Encoding if applied)**: "yes" = 1; "no" = 0

#### Paired Test\*

```{r}
paired_testing(paired_enc, var_name="water_collection_school_aged", 
               test_type = "mcnemar", plot_diff=FALSE)
```

```{r}
mcne
```

#### Regression - Community\*

```{r}
community_reg(df=paired_enc, 
              col_name="water_collection_school_aged", dep="-1", 
              title="Water Collection Responsibility (School-Aged) by Community", 
              exclude_outliers = TRUE, outliers = "feature",
              var_type="categorical", calc_diff =TRUE,
              diff_type="direction", customer_type="hs", 
              y_axis= "Households",
              sig_var="CAPEX_USD", unit_val = "HH/K", extra="USD")
```

#### Logistic Regression - Individual

```{r}
consumption_reg(df = paired_enc, reg_type ="logistic",
                dep= "water_collection_school_aged", 
                ind="avg_mon_consumption_period",
                calc_diff=TRUE, diff_type = "direction",
                x_axis="Avg. Monthly Consumption Pre-Post Period (kwH)", 
                y_axis="Water Collection Responsibility (School-Aged)",
                log_direction = -1,
                exclude_outliers = TRUE, outliers = "feature",
                title="Individual Directional Change vs Consumption")
```

### Cooking Fuel Collection Time

**Data Source**: Paired Household Surveys (Pre & Post)

**Value (Encoding if applied)**: "No need to collect fuel" = 1; "less than 1 hour" = 2; "1-2 hours" =3; "3-5 hours" = 4; "greater than 5 hours" = 5

#### Paired Test\*

```{r}
# How long does the cooking fuel collection process take on a daily basis?
paired_testing(paired_enc, var_name="cooking_fuel_collection_time", 
               test_type = "ttest", plot_diff=TRUE, 
               x_axis="Differences", y_axis="Count",
               remove_outliers = TRUE,
               plt_title="Difference in Pre-Post Cooking Fuel Collection Times")
```

#### Regression - Community

```{r}
## Community Paired Differences
# Directional 
community_reg(df=paired_enc, 
              col_name="cooking_fuel_collection_time", dep="-1", 
              var_type="categorical", 
              calc_diff = TRUE, diff_type = "direction",
              exclude_outliers = TRUE, outliers = "feature",
              customer_type="hs", y_axis= "Households",
              title="Decrease (Direction) in 
              Cooking Fuel Collection Time by Community",
              sig_var="CAPEX_USD", unit_val = "HH/K", extra="USD")

```

#### Linear Regression - Individual

```{r}
consumption_reg(df = paired_enc, reg_type ="linear",
                dep= "cooking_fuel_collection_time", 
                ind="avg_mon_consumption_period",
                calc_diff=TRUE, diff_type = "magnitude",
                x_axis="Avg. Monthly Energy Consumption Pre-Post Period (kwH)", 
                y_axis="Water Collection Time", 
                #threshold = 4, threshold_bound = "lower",
                title="Individual Directional Change vs Consumption")
```

#### Logistic Regression - Individual

```{r}
# Regression - Pre-Post Differences
consumption_reg(df = paired_enc, reg_type ="logistic",
                dep= "cooking_fuel_collection_time", 
                ind="avg_mon_consumption_period",
                calc_diff=TRUE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption Pre-Post Period (kwH)", 
                y_axis="Cooking Fuel Collection Time",
                log_direction = -1,
                exclude_outliers = TRUE, outliers = "feature",
                title="Individual Directional Change vs Consumption")

# Monthly consumption between pre and post: 
# avg_monthly_consumption = (365* (Consumption_period / no.of days))/12  
```

### TODO: Women-led Business Ownership

**Data Source**: Paired Household Surveys (Pre & Post)

**Value (Encoding if applied)**: Everything else = 0; "adult_female" = 1

#### Paired Test

```{r}
# Are any household members business owners? Isolate for those with 'adult_'female
print("All")
paired_testing(paired_enc, var_name="business_owners_female", 
               test_type = "mcnemar", plot_diff=FALSE)

```

#### Paired Test & Regression Community - Nigeria

```{r}
## Subgroup Analysis: Country
# Nigeria
print("Nigeria")
paired_testing(nigeria_paired_enc, var_name="business_owners_female", 
               test_type = "mcnemar", plot_diff=FALSE)
```

#### Paired Test & Regression Community - Kenya

```{r}
# Kenya
print("Kenya")
paired_testing(kenya_paired_enc, var_name="business_owners_female", 
               test_type = "mcnemar", plot_diff=FALSE)

community_reg(df=kenya_paired_enc, 
              col_name="business_owners_female", 
              dep="1", var_type="categorical", 
              calc_diff = TRUE, diff_type = "direction",
              exclude_outliers = TRUE, outliers = "feature",
              customer_type="hs", y_axis= "Households",
              title="New Female Business Owners Change by Community")
```

#### Paired Test by Gender

```{r}
## Subgroup Analysis: Country
# Women
print("Women")
gdr <- 1
gender_paired <- paired_enc %>% filter(gender_post == gdr)
paired_testing(gender_paired, var_name="business_owners_female", 
               test_type = "mcnemar", plot_diff=FALSE)

# Men
print("Men")
gdr <- 2
gender_paired <- paired_enc %>% filter(gender_post == gdr)
paired_testing(gender_paired, var_name="business_owners_female", 
               test_type = "mcnemar", plot_diff=FALSE)
```

#### Logistic Regression - Individual

```{r}
consumption_reg(df = paired_enc, reg_type ="logistic",
                dep= "business_owners_female", 
                ind="avg_mon_consumption_period",
                calc_diff=TRUE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption Pre-Post Period (kwH)", 
                y_axis="New Female Business Owners Change",
                log_direction = 1,
                #exclude_outliers = TRUE, outliers = "feature",
                title="Individual Directional Change vs Consumption")
```

### New Female workers

**Data Source**: Commercial & Institution Post Survey

**Value (Encoding if applied)**: Any value

#### Regression - Community\*

```{r}
ci_enc$hired_women <- ifelse(ci_enc$workforce_change_female > 0, 1, 0)
```

```{r}
# If you answered yes to adding new workers, how many new employees are female?
community_reg(df=ci_enc, 
              col_name="hired_women", 
              dep="1", var_type="categorical", 
              exclude_outliers = TRUE, outliers = "feature",
              customer_type="ci", y_axis= "Organizations \nReporting Increase",
              sig_var = "Customers", unit_val = "Orgs/Cust",extra=""
              #,title_sig="Increase in Employment For Women in Communities"
              )
```

#### Linear Regression - Individual

```{r}
# Regression - Pre-Post Differences
consumption_reg(df = ci_enc, reg_type ="linear",
                ind="avg_mon_consumption_cum",
                dep= "workforce_change_female", 
                exclude_outliers = TRUE, outliers = "feature",
                x_axis="Avg. Monthly Energy Consumption Cumulative (kwH)", 
                y_axis="Women Workers", to_remove=c(0),
                threshold = 4, threshold_bound = "lower",
                title="New Female Workers vs. Consumption")
```

#### Logistic Regression - Individual

```{r}
consumption_reg(df = ci_enc, reg_type ="logistic",
                dep= "hired_women", 
                ind="avg_mon_consumption_cum",
                calc_diff=FALSE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption Pre-Post Period (kwH)", 
                y_axis="New Female Workers",
                log_direction = 1,
                exclude_outliers = TRUE, outliers = "feature",
                title="Individual Directional Change vs Consumption")
```

# 3- Productivity

## A) Descriptive

### Power

#### Sources

```{r}
## What is your primary power source?
# Unpaired
compare_pre_post(df_pre=initial_pre, df_post=post_clean, lgd_title ="Types",
                 var_name="power_sources_primary", var_type="non_cont",
                 subplot_type="bar_simple", 
                 title="Unpaired: Primary Power Source")

# Paired
compare_paired(data=paired_clean,
               var_name="power_sources_primary",
               lgd_title="Source Type",
               plot_title="Paired: Pimary Power Source")
```

#### **Un-clean sources: Diesel, Petrol, Kerosene**

```{r}
## What is your primary power source?
# Unpaired
compare_pre_post(df_pre=initial_pre, df_post=post_clean, 
                 lgd_title ="Non-renewable?",
                 var_name="power_sources_unclean", var_type="non_cont",
                 subplot_type="pie", 
                 title="Unpaired: Breakdown of Power Sources (Non-Renewable)")

# Paired
generic_compare(data=paired_clean, var_type="non_cont",
               var1="power_sources_unclean_pre", 
               var2="power_sources_unclean_post", 
               lgd_title ="Non-renewable?",
               var1_title="Pre", var2_title="Post", 
               subplot_type="pie", 
               plot_title="Paired: Breakdown of Power Sources (Non-Renewable)")

# Paired
compare_paired(data=paired_clean,
               var_name="power_sources_unclean",
               lgd_title="Non-renewable?",
               plot_title="Paired: Change of Power Sources (Non-Renewable)")
```

### Light Hours

```{r}
## How many hours of light per day do you currently have at home?
# Unpaired
compare_pre_post(df_pre=initial_pre, df_post=post_clean, 
                 var_name="light_hours_current", var_type="cont",
                 subplot_type="hist", title="Light Hours",
                 char_remove=c(46, 200))
```

### Appliances

#### Count

```{r}
# How many electronic devices or appliances do you currently use in the household
compare_pre_post(df_pre=initial_pre, df_post=post_clean, 
                 var_name="appliances_count", var_type="cont",
                 exclude_outliers = TRUE, 
                 subplot_type="hist", title="Appliances")
```

#### Change

```{r}
# Has the number of electronic devices or appliances increased since connection to minigrid?
plot_func(df=post_clean, var_name="appliances_count_change", 
          var_type="non_cont", lgd = "Change",
          plot_title="Change in No. of Appliances", 
          plot_type="bar_simple")
```

#### Charging Sources

```{r}
# What is your primary power source?
compare_pre_post(df_pre=initial_pre, df_post=post_clean, lgd_title ="Types",
                 var_name="applicances_charging_sources", var_type="non_cont",
                 subplot_type="bar_simple", 
                 title="Unpaired: Appliances Charging Source")

compare_paired(data=paired_clean,
               var_name="applicances_charging_sources",
               lgd_title="Source Type",
               plot_title="Paired: Appliances Charging Source")
```

### Phone Charging

#### Frequency

```{r}
## How often do you need to charge your mobile phone?
# Unpaired
compare_pre_post(df_pre=initial_pre, df_post=post_clean, 
                 var_name="phone_charge_frequency", var_type="non_cont",
                 subplot_type="bar_simple", lgd_title = "Time Intervals",
                 title="Unpaired: Phone Charging Frequency")

# Paired
compare_paired(data=paired_clean,
               var_name="phone_charge_frequency",
               lgd_title="Time Intervals",
               plot_title="Paired: Phone Charging Frequency")
```

#### Location

```{r}
## Where do you typically charge your mobile phone?
# Unpaired
compare_pre_post(df_pre=initial_pre, df_post=post_clean, 
                 var_name="phone_charge_location", var_type="non_cont",
                 subplot_type="bar_simple", lgd_title = "Places",
                 title="Unpaired: Location of Phone Charging")

# Paired
compare_paired(data=paired_clean,
               var_name="phone_charge_location",
               lgd_title="Places",
               plot_title="Paired: Location of Phone Charging")
```

#### Travel Distance

```{r}
# How far must you travel to charge your mobile phone?
compare_pre_post(df_pre=initial_pre, df_post=post_clean, 
                 var_name="phone_charge_travel_distance", var_type="non_cont",
                 subplot_type="bar_simple", lgd_title = "Distances",
                 title="Unpaired: Travel Distance to Charge Phone",
                 char_remove=NULL)

# Paired
compare_paired(data=paired_clean,
               var_name="phone_charge_travel_distance",
               lgd_title="Time Intervals",
               plot_title="Paired: Travel Distance to Charge Phone")
```

### Water Collection

#### Travel Distance

```{r}
## How far must you travel to obtain your water supply?
# Unpaired
compare_pre_post(df_pre=initial_pre, df_post=post_clean, 
                 var_name="water_collection_travel_distance", var_type="non_cont",
                 subplot_type="bar_simple", lgd_title = "Distances",
                 title="Travel Distance for Water Collection")

# Paired
compare_paired(data=paired_clean,
               var_name="water_collection_travel_distance",
               lgd_title="Time Intervals",
               plot_title="Paired: Travel Distance for Water Collection")
```

#### Time

```{r}
# Unpaired
compare_pre_post(df_pre=initial_pre, df_post=post_clean,
                 var_name="water_collection_time", 
                 var_type="non_cont",
                 subplot_type="pie",
                 lgd_title="Time Intervals",
                 title="Unpaired: Water Collection Time")

# Paired
compare_paired(data=paired_clean,
               var_name="water_collection_time",
               lgd_title="Time Intervals",
               plot_title="Paired: Water Collection Time")
```

### Clinic Travel Distance

```{r}
## How close is the nearest Health Center / Clinic
# Unpaired
compare_pre_post(df_pre=initial_pre, df_post=post_clean, 
                 var_name="clinic_travel_distance", var_type="non_cont",
                 subplot_type="bar_simple", lgd_title = "Distances",
                 title="Travel Distance  To Nearest Clinic")

# Paired
compare_paired(data=paired_clean,
               var_name="clinic_travel_distance",
               lgd_title="Time Intervals",
               plot_title="Paired: Travel Distance To Nearest Clinic")
```

### Cooking Fuel

#### Sources

```{r}
## What is your main source of energy for cooking?
# Unpaired
compare_pre_post(df_pre=initial_pre, df_post=post_clean, lgd_title ="Types",
                 var_name="cooking_energy_sources", var_type="non_cont",
                 subplot_type="bar_simple", 
                 title="Unpaired: Cooking Energy Sources")

# Paired
compare_paired(data=paired_clean,
               var_name="cooking_energy_sources",
               lgd_title="Types",
               plot_title="Paired: Cooking Energy Sources")
```

#### **Un-clean sources: Kerosene, Charcoal**

#### Time

```{r}
##  How long does the cooking fuel collection process take on a daily basis?
# Unpaired
compare_pre_post(df_pre=initial_pre, df_post=post_clean,
                 var_name="cooking_fuel_collection_time", 
                 var_type="non_cont",
                 subplot_type="pie",
                 lgd_title="Time Intervals",
                 title="Unpaired: Cooking Fuel Collection Time")

# Paired
compare_paired(data=paired_clean,
               var_name="cooking_fuel_collection_time",
               lgd_title="Time Intervals",
               plot_title="Paired: Cooking Fuel Collection Time")
```

### Households - Academic Performance

```{r}
# Has school performance changed since connection to minigrid?
plot_func(df=post_clean, var_name="school_performance_change", 
          var_type="non_cont", lgd = "Change",
          plot_title="Unpaired: Household - Academic Performance", 
          plot_type="bar_simple")

# Paired
plot_func(df=paired_clean, var_name="school_performance_change", 
          var_type="non_cont", lgd = "Change",
          plot_title="Paired: Household - Academic Performance", 
          plot_type="bar_simple")
```

### Schools - Academic Performance

```{r}
plot_func(df=schools_clean, var_name="school_performance", 
          var_type="non_cont", lgd = "Change",
          plot_title="Schools - Academic Performance", 
          plot_type="pie")
```

### Commercial & Institution

#### Operation Hours Change

```{r}
# Since connection to Renewvia minigrid, have your hours of operation changed at all?
plot_func(df=ci_clean, var_name="operations_hours_change", 
          var_type="non_cont", lgd="Change",
          plot_title="Change in C&I Business Hours", 
          plot_type="pie")
```

#### Additional Operation Hours

```{r}
plot_func(df=ci_clean, var_name="business_hours_increase", 
          var_type="non_cont", lgd="By how much?",
          plot_title="C&I Added Operation Hours", 
          plot_type="pie")
```

#### Change in Workforce

```{r}
# Since connection to Renewvia mingrid, have you had any change in number of workers/employees at your place of work?
plot_func(df=ci_clean, var_name="workforce_change", 
          var_type="non_cont", lgd="Change",
          plot_title="Change in C&I Workforce", 
          plot_type="pie")
```

#### Adding New Products/Services

```{r}
# Have you added any new products or services since connection to Renewvia minigrid?
plot_func(df=ci_clean, var_name="ci_offering_change", 
          var_type="non_cont", lgd="Change",
          plot_title="Change in C&I Products/Services", 
          plot_type="pie")
```

### TODO

-   Annotation & encoding of "light_primary_source"

-   For cooking energy sources, add the unclean sources: charcoal, firewood

### 

## B) Inferential

### Power Source

**Data Source**: Paired Household Surveys (Pre & Post)

**Value (Encoding if applied)**: "yes" = 1; "no" = 0

#### Paired Test\*

```{r}
## What is your primary power source? Binarized as renewable vs. non-renewable sources (Diesel, Petrol, Kerosene)
paired_testing(paired_enc, var_name="power_sources_unclean", 
               test_type = "mcnemar", plot_diff=FALSE)
```

#### Regression - Community\*

```{r}
community_reg(df=paired_enc, 
              col_name="power_sources_unclean", dep="-1", 
              title="Power Source (Non-Renewable) by Community", 
              exclude_outliers = TRUE, outliers = "feature",
              var_type="categorical", calc_diff =TRUE,
              diff_type="direction", customer_type="hs", 
              y_axis= "Households \nReporting Decrease",
              sig_var = "Customers", unit_val = "HH/Cust", extra=""
              #<title_sig="Decrease of Non-Renewable Power Sources Usage in Communities"
              )
```

#### Linear Regression - Individual

#### Logistic Regression - Individual

```{r}
consumption_reg(df = paired_enc, reg_type ="logistic",
                dep= "power_sources_unclean", 
                ind="avg_mon_consumption_period",
                calc_diff=TRUE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption Pre-Post Period (kwH)", 
                y_axis="Unclean Power Sources",
                log_direction = -1,
                exclude_outliers = TRUE, outliers = "feature",
                title="Individual Directional Change vs Consumption")
```

### No. of Appliances

**Data Source**: Paired Household Surveys (Pre & Post)

**Value (Encoding if applied)**: Any numeric value

#### Paired Test\*

```{r}
paired_testing(paired_enc, var_name = "appliances_count", 
               plot_diff = TRUE, 
               test_type="ttest", remove_outliers=TRUE,
               x_axis="Differences", y_axis="Count",
               plt_title="Difference in Pre-Post House Appliances")
```

#### Regression - Community\*

```{r}
community_reg(df=paired_enc, 
              col_name="appliances_count", dep="1", 
              title="Power Source (Non-Renewable) by Community", 
              exclude_outliers = TRUE, outliers = "feature",
              var_type="categorical", calc_diff =TRUE,
              diff_type="direction", customer_type="hs", 
              y_axis= "Households \nReporting Increase",
              sig_var = "Customers", unit_val = "HH/Cust", 
              extra=""
              #title_sig="Increase of Appliances Owned in Communities"
              )
```

#### Logistic Regression - Individual

```{r}
consumption_reg(df = paired_enc, reg_type ="logistic",
                dep= "appliances_count", 
                ind="avg_mon_consumption_period",
                calc_diff=TRUE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption Pre-Post Period (kwH)", 
                y_axis="No. of Appliances",
                log_direction = 1,
                exclude_outliers = TRUE, outliers = "feature",
                title="Individual Directional Change vs Consumption")
```

### Light Hours

**Data Source**: Paired Household Surveys (Pre & Post)

**Value (Encoding if applied)**: Any numeric value between 0 and 24

#### Paired Test\*

```{r}
## How many hours of light per day do you currently have at home?
reg_temp <- paired_enc %>% filter(!light_hours_current_pre %in% c(46, 25) |
                                  !light_hours_current_post %in% c(200))
paired_testing(reg_temp, var_name = "light_hours_current", 
               plot_diff = TRUE, 
               test_type="ttest", 
               remove_outliers=TRUE,
               x_axis="Differences", y_axis="Count",
               plt_title="Difference in Pre-Post House Light Hours")
```

#### Regression - Community\*

```{r}
community_reg(df=paired_enc, 
              col_name="light_hours_current", dep="1", 
              title="Light Hours by Community", 
              exclude_outliers = TRUE, outliers = "feature",
              var_type="categorical", calc_diff =TRUE,
              diff_type="direction", customer_type="hs", 
              y_axis= "Households")
```

### Phone Charging Travel Distance

**Data Source**: Paired Household Surveys (Pre & Post)

**Value (Encoding if applied)**: "no_travel" = 0, "less_than_1_km" = 1, "1_2_km" = 2, "2_5_km"= 3, "5_10_km" = 4, "greater_than_10_km" = 5

#### Paired Test\*

unique(paired_enc\$phone_charge_travel_distance_post)

```{r}
paired_testing(paired_enc, var_name="phone_charge_travel_distance", 
               test_type = "wilcoxon", x_axis="Differences", y_axis="Count",
               plt_title="Difference in Pre-Post Phone Charging Traveling Distance",
               plot_diff=TRUE, 
               #remove_outliers = TRUE
               )
```

#### Regression - Community

```{r}
community_reg(df=paired_enc, 
              col_name="phone_charge_travel_distance", dep="-1", 
              title="Phone Travel Distance by Community", 
              exclude_outliers = TRUE, outliers = "feature",
              var_type="categorical", calc_diff =TRUE,
              diff_type="direction", customer_type="hs", 
              y_axis= "Households",
              sig_var = "Customers", unit_val = "HH/Cust", 
              extra="")
```

#### Logistic Regression - Individual

```{r}
consumption_reg(df = paired_enc, reg_type ="logistic",
                dep= "phone_charge_travel_distance", 
                ind="avg_mon_consumption_period",
                calc_diff=TRUE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption Pre-Post Period (kwH)", 
                y_axis="Change (Decrease)",
                log_direction = -1,
                exclude_outliers = TRUE, outliers = "feature",
                title="Phone Charging Travel Distance vs Consumption")
```

### Water Collection Travel Distance

**Data Source**: Paired Household Surveys (Pre & Post)

**Value (Encoding if applied)**: "nothing" = 0, "no_travel" = 0, "less_than_1_km" = 1, "1_2_km" = 2, "2_5_km"= 3, "5_10_km" = 4, "greater_than_10_km" = 5

#### Paired Test\*

```{r}
paired_testing(paired_enc, var_name="water_collection_travel_distance", 
               test_type = "wilcoxon", x_axis="Differences", y_axis="Count",
               plt_title="Difference in Pre-Post Water Collection Distance",
               plot_diff=TRUE, 
               #remove_outliers = TRUE
               )
```

#### Regression - Community

```{r}
community_reg(df=paired_enc,                
              col_name="water_collection_travel_distance", 
              dep="-1", 
              title="Water Collection Travel Distance (Decrease) by Community", 
              exclude_outliers = TRUE, outliers = "feature",               
              var_type="categorical", calc_diff =TRUE,               
              diff_type="direction", customer_type="hs",                
              y_axis= "Households",
              sig_var = "Customers", unit_val = "HH/Cust", 
              extra="")
```

#### Logistic Regression - Individual

```{r}
consumption_reg(df = paired_enc, reg_type ="logistic",
                dep= "water_collection_travel_distance", 
                ind="avg_mon_consumption_period",
                calc_diff=TRUE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption Pre-Post Period (kwH)", 
                y_axis="Change (Decrease)",
                log_direction = -1,
                exclude_outliers = TRUE, outliers = "feature",
                title="Water Collection Travel Distance vs Consumption")
```

### Clinic Travel Distance

**Data Source**: Paired Household Surveys (Pre & Post)

**Value (Encoding if applied)**: "no_travel" = 0,"less_than_1_km" = 1, "between_1_2_km" = 2, "between_2_3_km" = 3, "between_3_5_km" = 4, "greater_than_5_km" = 5

#### Paired Test

```{r}
paired_testing(paired_enc, var_name="clinic_travel_distance", 
               test_type = "wilcoxon", x_axis="Differences", y_axis="Count",
               plt_title="Difference in Pre-Post Clinic Travel Distance",
               plot_diff=TRUE, remove_outliers = TRUE)
```

### Households - Academic Performance

**Data Source**: Household Post-Survey

**Value (Encoding if applied)**: "Yes, they have increased" = 1, "Yes, they have decreased" = -1, "No, it is pretty much the same" = 0

#### Regression - Community\*

```{r}
# Has school performance changed since connection to minigrid?
community_reg(df=post_enc, 
              col_name="school_performance_change", 
              dep="1", var_type="categorical",
              exclude_outliers = TRUE, outliers = "feature",
              customer_type="hs", y_axis= "Households \nReporting Improvement",
              sig_var = "CAPEX_USD", unit_val = "HH/K", extra="USD"
              #title_sig="Increase of Academic Performance in Communities"
              )
```

#### TODO: Logistic Regression - Individual\*

```{r}
# Found an undesired effect
consumption_reg(df = post_enc, reg_type ="logistic",
                dep= "school_performance_change", 
                ind="avg_mon_consumption_period",
                #calc_diff=FALSE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption Pre-Post Period (kwH)", 
                y_axis="Households - School Performance Change",
                log_direction = 1,
                exclude_outliers = TRUE, outliers = "feature",
                title="Individual Directional Change vs Consumption")
```

```{r}
consumption_reg(df = post_enc, reg_type ="logistic",
                dep= "school_performance_change", 
                ind="avg_mon_consumption_cum",
                #calc_diff=FALSE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption Cumulative (kwH)", 
                y_axis="Households - School Performance Change",
                log_direction = 1,
                exclude_outliers = TRUE, outliers = "feature",
                title="Individual Directional Change vs Consumption")
```

### Schools - Academic Performance

**Data Source**: C&I Post-Survey

**Value (Encoding if applied)**: "Yes, they have increased" = 1, "Yes, they have decreased" = -1, "No, it is pretty much the same" = 0

#### Regression - Community\*

```{r}
## Have you seen a change in overall school performance?
community_reg(df=schools_enc, 
              col_name="school_performance", dep="1", var_type="categorical",
              exclude_outliers = TRUE, outliers = "feature",
              customer_type="school", y_axis= "Schools \nReporting Improvement",
              title="Schools - Increase in Academic Performace by Community",
              sig_var = "PV_Size_kWp", unit_val = "Schools/kWp", extra=""
              #title_sig="Increase of Academic Performance in Communities"
              )
```

### Operation Hours Change

**Data Source**: C&I Post-Survey

**Value (Encoding if applied)**: "Yes, they have increased" = 1, "Yes, they have decreased" = -1, "No, it is pretty much the same" = 0

#### Regression - Community

```{r}
## Since connection to Renewvia mini-grid, have your hours of operation changed at all?
community_reg(df=ci_enc, 
              col_name="operations_hours_change", 
              dep="1", var_type="categorical",
              exclude_outliers = TRUE, outliers = "feature",
              customer_type="ci", y_axis= "C&I",
              title="Increase in Operation Hours by Community",
              sig_var = "CAPEX_USD", unit_val = "HH/K", extra="USD")
```

#### TODO: Logistic Regression - Individual

```{r}
consumption_reg(df = ci_enc, reg_type ="logistic",
                dep= "operations_hours_change", 
                ind="avg_mon_consumption_cum",
                #calc_diff=FALSE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption Cumulative (kwH)", 
                y_axis="Hours of Operations Change",
                log_direction = 1,
                exclude_outliers = TRUE, outliers = "feature",
                title="Individual Directional Change vs Consumption")
```

### Workforce Change

**Data Source**: C&I Post-Survey

**Value (Encoding if applied)**: "Yes, we have added workers" = 1, "Yes, we have lost workers" = -1, "No, the number has remained the same" = 0

#### Regression - Community\*

```{r}
# Since connection to Renewvia mini-grid, have you had any change in number of workers/employees at your place of work?
community_reg(df=business_enc, 
              col_name="workforce_change", 
              dep="1", var_type="categorical",
              exclude_outliers = TRUE, outliers = "feature",
              customer_type="ci", y_axis= "Organizations \nReporting Increase",
              title="Increase in C&I's Workforce by Community",
              sig_var = "Customers", unit_val = "HH/Cust", extra="")
```

#### Logistic Regression - Individual

```{r}
consumption_reg(df = business_enc, reg_type ="logistic",
                dep= "workforce_change", 
                ind="avg_mon_consumption_cum",
                #calc_diff=FALSE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption Cumulative (kwH)", 
                y_axis="Workforce Change",
                log_direction = 1,
                exclude_outliers = TRUE, outliers = "feature",
                title="Individual Directional Change vs Consumption")
```

### Adding New Products/Services

**Data Source**: C&I Post-Survey

**Value (Encoding if applied)**: "Yes" = 1, "No" = 0

#### Regression - Community\*

```{r}
# Have you added any new products or services since connection to Renewvia minigrid?
community_reg(df=ci_enc, 
              col_name="ci_offering_change", 
              dep="1", var_type="categorical",
              exclude_outliers = TRUE, outliers = "feature",
              customer_type="ci", y_axis= "Organizations \nReporting Increase",
              title="Newly Added Offerings by Community",
              #title_sig="Increase of  Business Offering in Communities"
              sig_var = "PV_Size_kWp", unit_val = "Orgs/kWp", extra="")
```

#### Logistic Regression - Individual

```{r}
consumption_reg(df=ci_enc, reg_type ="logistic",
                dep= "ci_offering_change", ind="avg_mon_consumption_cum",
                #calc_diff=FALSE, diff_type = "direction",
                exclude_outliers = TRUE, outliers = "feature",
                x_axis="Avg. Monthly Energy Consumption Cumulative (kwH)", 
                y_axis="Product Offering Change", log_direction = 1,
                title="Newly Added Offerings vs. Energy Consumption")
```

### Visualize Significant Results

```{r, fig.width=12, fig.height=8}
violins(data = paired_enc, 
        var_names = c("light_hours_current", 
                      "appliances_count",
                      "phone_charge_travel_distance",
                      "water_collection_travel_distance"))
```

# 4- Health & Well-Being

## A) Descriptive

### Water

#### All Sources

```{r}
## What is your source of water?
# Unpaired
compare_pre_post(df_pre=initial_pre, df_post=post_clean, 
                 var_name="water_source", var_type="non_cont",
                 subplot_type="bar_simple", lgd_title = "Sources",
                 title="Unpaired: Water Sources",
                 char_remove=NULL)

# Paired
compare_paired(data=paired_clean,
               var_name="water_source",
               lgd_title="Sources",
               plot_title="Paired: Water Sources")
```

#### Access to Clean Drinking Water

```{r}
# Do you have a source for clean drinking water?
# Unpaired
compare_pre_post(df_pre=initial_pre, df_post=post_clean, 
                 var_name="clean_drinking_water", var_type="non_cont",
                 subplot_type="pie", 
                 lgd_title = "Accessible?",
                 title="Unpaired: Breakdown of Clean Drinking Water Access")

# Paired
generic_compare(data=paired_clean, var_type="non_cont",
               var1="clean_drinking_water_pre", 
               var2="clean_drinking_water_post", 
               lgd_title ="Accessible?",
               var1_title="Pre", var2_title="Post", 
               subplot_type="pie", 
               plot_title="Paired: Breakdown of Clean Drinking Water Access")

# Paired
compare_paired(data=paired_clean,
               var_name="clean_drinking_water",
               lgd_title="Accessible?",
               plot_title="Paired: Chnage in Clean Drinking Water Access")
```

#### Clean Sources

```{r}
# What is the source for clean drinking water?
# Unpaired
compare_pre_post(df_pre=initial_pre, df_post=post_clean, 
                 var_name="clean_drinking_water_source", var_type="non_cont",
                 subplot_type="bar_simple", 
                 lgd_title = "Do you have clean drinking water?",
                 title="Unpaired: Clean Drinking Water Sources")

# Paired
compare_paired(data=paired_clean,
               var_name="clean_drinking_water_source",
               lgd_title="Do you have clean drinking water?",
               plot_title="Paired: Clean Drinking Water Sources")
```

### Kerosene Lamps

#### Count

```{r}
# How many kerosene lamps do you currently have in your household?
compare_pre_post(df_pre=initial_pre, df_post=post_clean, 
                 var_name="kerosene_lamps_count", var_type="cont",
                 subplot_type="hist", exclude_outliers = TRUE, 
                 title="Unpaired: No. of Kerosene Lamps",
                 char_remove=c(24))
```

#### Usage Change

```{r}
# Has the number of kerosene lamps in your household changed since connection to minigrid?
plot_func(df=post_clean, var_name="kerosene_lamp_usage_change", lgd ="Change", 
          var_type="non_cont", plot_title="Kerosene Lamps Usage", 
          plot_type="bar_simple")
```

### Healthcare

#### Clinic's Electricity

```{r}
# # Does your Health Center have access to electricity?
# Unpaired
compare_pre_post(df_pre=initial_pre, df_post=post_clean, 
                 var_name="clinic_electricity_access", var_type="non_cont",
                 subplot_type="pie", 
                 lgd_title = "Electrified?",
                 title="Unpaired: Breakdown of Clinic Access To Electricity")

# Paired
generic_compare(data=paired_clean, var_type="non_cont",
               var1="clinic_electricity_access_pre", 
               var2="clinic_electricity_access_post", 
               lgd_title ="Electrified?",
               var1_title="Pre", var2_title="Post", 
               subplot_type="pie", 
               plot_title="Paired: Breakdown of of Clinic Access To Electricity")

# Paired
compare_paired(data=paired_clean,
               var_name="clinic_electricity_access",
               lgd_title="Electrified?",
               plot_title="Paired: Change in Clinic Access To Electricity")
```

#### Clinic Travel Distance

```{r}
## How close is the nearest Health Center / Clinic
# Unpaired
compare_pre_post(df_pre=initial_pre, df_post=post_clean, 
                 var_name="clinic_travel_distance", var_type="non_cont",
                 subplot_type="bar_simple", 
                 lgd_title = "Distances",
                 title="Unpaired: Clinic Travel Distance")


# Paired
compare_paired(data=paired_clean,
               var_name="clinic_travel_distance",
               lgd_title="Distances",
               plot_title="Paired: Clinic Travel Distance")
```

#### Clinic's Refrigeration

```{r}
# Does your Health Center / Clinic have access to refrigeration?
# Unpaired
compare_pre_post(df_pre=initial_pre, df_post=post_clean, 
                 var_name="clinic_refrigeration_access", var_type="non_cont",
                 subplot_type="pie", 
                 lgd_title = "Has refrigeration?",
                 title="Unpaired: Clinic Access to Refrigeration")

# Paired
generic_compare(data=paired_clean, var_type="non_cont",
               var1="clinic_refrigeration_access_pre", 
               var2="clinic_refrigeration_access_post", 
               lgd_title ="Has refrigeration?",
               var1_title="Pre", var2_title="Post", 
               subplot_type="pie", 
               plot_title="Paired: Breakdown of of Clinic Access to Refrigeration")

# Paired
compare_paired(data=paired_clean,
               var_name="clinic_refrigeration_access",
               lgd_title="Has refrigeration?",
               plot_title="Paired: Change in Clinic Access to Refrigeration")
```

#### New Health Services

```{r}
plot_func(df=clinic_clean, var_name="health_offering_change_count", 
          var_type="non_cont", plot_title="No. of New Health Services", 
          plot_type="bar_simple", lgd="No. of Health Services" 
          #char_remove = 0
          )
```

```{r}
# What is the Clinic / Hospital able to offer or provide due to connection to Renewvia minigrid that it wasnt able to offer before?
plot_func(df=clinic_clean, var_name="health_offering_change_count", 
          var_type="cont", plot_title="No. of New Health Services", 
          plot_type="hist")
```

#### Types of Services

```{r}
# What were those added services?
wait <- sum(ci_clean$shorter_wait, na.rm = TRUE)
vaccines <- sum(ci_clean$vaccine_cold_storage, na.rm = TRUE)
patients <- sum(ci_clean$more_patients_treated, na.rm = TRUE)
hours <- sum(ci_clean$clinic_longer_hours, na.rm = TRUE)

vals <- c(wait, vaccines, patients, hours)

# creating matrix
tab <- as.data.frame(as.matrix(vals), 
                     row.names = c("Shorter.Wait.Times", 
                                   "Vaccines.Cold.Storage", 
                                   "More.Patients", 
                                   "Longer.Hours"))
setnames(tab, old = c('V1'),
          new = c("Count"))
# t(tab)
tab
```

### Life Improvement

```{r}
# Would you say that having access to minigrid power has improved your quality of life?
plot_func(df=post_clean, var_name="minigrid_access_life_improvement", 
          var_type="non_cont", plot_title="Life Improvement", 
          plot_type="bar_simple", lgd="Any change?")
```

## B) Inferential

### Access to clean drinking water

**Data Source**: Paired Household Surveys (Pre & Post)

**Value (Encoding if applied)**: "yes" = 1; "no" = 0

#### Paired Test\*

```{r}
# Do you have a source for clean drinking water?
paired_testing(paired_enc, var_name="clean_drinking_water", 
               test_type = "mcnemar", plot_diff=FALSE)
```

#### Regression - Community

```{r}
# Regression - Pre-Post Differences
community_reg(df=paired_enc, 
              col_name="clean_drinking_water", dep="1", 
              var_type="categorical", 
              calc_diff = TRUE,diff_type="direction",
              exclude_outliers = TRUE, 
              customer_type="hs", y_axis= "Households",
              sig_var = "CAPEX_USD", unit_val = "HH/K", extra="USD")
```

#### Logistic Regression - Individual

```{r}
consumption_reg(df=paired_enc,  reg_type ="logistic",
                dep="clean_drinking_water", ind="avg_mon_consumption_period",
                exclude_outliers = TRUE, outliers = "feature",
                calc_diff=TRUE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption Cumulative (kWh)", 
                y_axis="Access Change", log_direction = 1,
                title="Access To Clean Drinking Water vs. Energy Consumption")
```

### Kerosene Lamps

**Data Source**: Paired Household Surveys (Pre & Post)

**Value (Encoding if applied)**: Any numeric value

#### Paired Test\*

```{r}
## How many kerosene lamps do you currently use in your household? 
paired_testing(paired_enc, var_name="kerosene_lamps_count", 
               test_type = "ttest", x_axis="Differences", y_axis="Count",
               plt_title="Difference in Pre-Post Kerosone Lamps",
               plot_diff=TRUE, remove_outliers = TRUE)
```

#### Regression - Community

```{r}
community_reg(df=paired_enc, 
              col_name="kerosene_lamps_count", dep="-1", 
              title="Difference in Kerosene Lamps by Community", 
              var_type="categorical", 
              calc_diff = TRUE, diff_type="direction",
              exclude_outliers = TRUE,
              customer_type="hs", y_axis= "Households",
              sig_var = "CAPEX_USD", unit_val = "HH/K", extra="USD")
```

#### TODO: Regression - Consumption\*

```{r}
# Differences in period
consumption_reg(df = paired_enc, reg_type ="linear",
                dep= "kerosene_lamps_count", 
                ind="avg_mon_consumption_period",
                calc_diff=TRUE, diff_type="magnitude",
                exclude_outliers = TRUE, outliers = "dependent", 
                to_remove = c(0),
                # threshold = -4, threshold_bound = "higher",
                x_axis="Avg. Monthly Energy Consumption In Period (kWh)", 
                y_axis="Usage Change", 
                title="Difference Kersone Lamps Use vs. Consumption")
```

```{r}
# Post use
consumption_reg(df = post_enc, reg_type ="linear",
                dep= "kerosene_lamps_count", 
                ind="avg_mon_consumption_cum",
                #calc_diff=TRUE, diff_type="magnitude",
                exclude_outliers = TRUE, outliers = "dependent", 
                to_remove = c(0),
                # threshold = -4, threshold_bound = "higher",
                x_axis="Avg. Monthly Energy Consumption In Period (kWh)", 
                y_axis="No. of Kerosene Lamps", 
                title="Kerosene Use vs. Consumption")
```

#### TODO: Logistic Regression - Individual\*

```{r}
consumption_reg(df=paired_enc,  reg_type ="logistic",
                dep="kerosene_lamps_count", ind="avg_mon_consumption_period",
                exclude_outliers = TRUE, outliers = "feature",
                calc_diff=TRUE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption In Period (kWh)", 
                y_axis="Usage Change (Decrease)", log_direction = -1,
                title="Kerosene Lamps Usage vs. Energy Consumption")
```

### Kerosene Lamps Usage

**Data Source**: Household Post Survey

**Value (Encoding if applied)**: "Yes, it's decreased" = -1; "No, it's the same" = 0; "Yes, it's increased" = 1

#### Regression - Community\*

```{r}
community_reg(df=post_enc, 
              col_name="kerosene_lamp_usage_change", dep="-1", 
              var_type="categorical",
              exclude_outliers = TRUE, outliers = "feature", 
              title="Decrease in Kerosene Lamps Usage by Community",
              customer_type="hs", y_axis= "Households \nReporting Decrease",
              sig_var = "Customers", unit_val = "HH/Cust",extra="")
          
```

#### Logistic Regression - Individual

```{r}
consumption_reg(df=post_enc,  reg_type ="logistic",
                dep="kerosene_lamp_usage_change", ind="avg_mon_consumption_cum",
                exclude_outliers = TRUE, outliers = "feature",
                #calc_diff=TRUE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption In Period (kWh)", 
                y_axis="Usage Change (Decrease)", log_direction = -1,
                title="Kerosene Lamps Usage vs. Energy Consumption")
```

### New Health Services

**Data Source**: Commercial & Institution Post Survey

**Value (Encoding if applied)**: Any value

#### Regression - Community

```{r}
## For clinics or health services only: Since connection to Renewvia mini-grid, have your health service offerings changed in any of the following ways: (select all that apply).
community_reg(df=clinic_enc, 
              col_name="health_offering_change_count", dep="V1", 
              exclude_outliers = TRUE, outliers = "feature", 
              title="New Health Services Offered in Communities", 
              var_type="ratio", to_remove =c(0),
              customer_type="clinic", y_axis= "Clinics",
              sig_var = "Customers", unit_val = "HH/Cust",extra="USD")
```

#### Logistic Regression - Individual

```{r}
clinic_enc$health_add <- ifelse(clinic_enc$health_offering_change_count > 0, 1, 0)
consumption_reg(df=clinic_enc,  reg_type ="logistic",
                dep="health_add", 
                ind="avg_mon_consumption_cum",
                exclude_outliers = TRUE, outliers = "feature",
                #calc_diff=TRUE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption Cumulative (kWh)", 
                y_axis="Health Services (Increase)", log_direction = 1,
                title="Health Service Offering vs. Consumption")
```

### Clinic Access To Electricity

**Data Source**: Paired Household Surveys (Pre & Post)

**Value (Encoding if applied)**: "yes" = 1; "no" = 0

#### Paired Test\*

```{r}
## Does your Health Center / Clinic have access to electricity?
paired_testing(paired_enc, var_name="clinic_electricity_access", 
               test_type = "mcnemar", plot_diff=FALSE)
```

#### Logistic Regression - Individual

```{r}
consumption_reg(df=paired_enc,  reg_type ="logistic",
                dep="clinic_electricity_access", 
                ind="avg_mon_consumption_period",
                exclude_outliers = TRUE, outliers = "feature",
                calc_diff=TRUE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption In Period (kWh)", 
                y_axis="Access Change (Increase)", log_direction = 1,
                title="Clinic's Electricity Access vs. Consumption")
```

### Clinic Access To Refrigeration

**Data Source**: Paired Household Surveys (Pre & Post)

**Value (Encoding if applied)**: "yes" = 1; "no" = 0

#### Paired Test\*

```{r}
## Does your Health Center / Clinic have access to refrigeration?
paired_testing(paired_enc, var_name="clinic_refrigeration_access", 
               test_type = "mcnemar", plot_diff=FALSE)
```

#### Logistic Regression - Individual

```{r}
consumption_reg(df=paired_enc,  reg_type ="logistic",
                dep="clinic_refrigeration_access", 
                ind="avg_mon_consumption_period",
                exclude_outliers = TRUE, outliers = "feature",
                calc_diff=TRUE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption In Period (kWh)", 
                y_axis="Access Change (Increase)", log_direction = 1,
                title="Clinic's Refrigeration Access vs. Consumption")
```

### TODO: Better access to healthcare

**Data Source**: Household Post-Survey

**Value (Encoding if applied)**: "yes" = 1; "no" = 0

#### Regression - Community\*

```{r}
# Do you feel that you have better access to health services because of connection to minigrid?
community_reg(df=post_enc, 
              col_name="better_access_health_minigrid", 
              dep="1", var_type="categorical",
              exclude_outliers = TRUE, 
              #  outliers = "feature", 
              title="Better Healthcare Access by Community",
              customer_type="hs", y_axis= "Households \n Reporting Improvement",
              sig_var="Customers", unit_val = "HH/Cust", extra=""
                #title_sig="Better Access To Healthcare in Communities"
              ) 
```

#### Logistic Regression - Individual

```{r}
consumption_reg(df=post_enc,  reg_type ="logistic",
                dep="better_access_health_minigrid", 
                ind="avg_mon_consumption_cum",
                exclude_outliers = TRUE, outliers = "feature",
                #calc_diff=TRUE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption Cumulative (kWh)", 
                y_axis="Access Change (Increase)", log_direction = 1,
                title="Better Access To Healthcare vs. Consumption")
```

### Life Improvement

**Data Source**: Household Post-Survey

**Value (Encoding if applied)**: "yes" = 1; "no" = 0

#### Regression - Community\*

```{r}
community_reg(df=post_enc, 
              col_name="minigrid_access_life_improvement", 
              dep="1", var_type="categorical",
              exclude_outliers = TRUE, 
              #  outliers = "feature", 
              sig_var = "Customers", unit_val = "HH/Cust", extra="", 
              title="Life Improvement by Community",
              customer_type="hs", y_axis= "Households \nReporting Improvement") 
```

#### Logistic Regression - Individual

```{r}
consumption_reg(df=post_enc,  reg_type ="logistic",
                dep="minigrid_access_life_improvement", 
                ind="avg_mon_consumption_cum",
                exclude_outliers = TRUE, outliers = "feature",
                #calc_diff=TRUE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption Cumulative (kWh)", 
                y_axis="Change (Increase)", log_direction = 1,
                title="Life Improvement vs. Consumption")
```

```         
```

# 5- Safety

## A) Descriptive

### Feeling Safe

```{r}
# How safe do you feel outside your home when it is dark?
# Unpaired
compare_pre_post(df_pre=initial_pre, df_post=post_clean, 
                 var_name="feel_safe_dark", var_type="non_cont",
                 subplot_type="bar_simple", lgd_title = "Scores",
                 title="Unpaired: Feeling Safe When Dark")

# Paired
compare_paired(data=paired_clean,
               var_name="feel_safe_dark",
               lgd_title="Score",
               plot_title="Paired: Feeling Safe When Dark")
```

```{r}
for(i in 1: 5) {
  safe_i <- paired_enc %>% filter(feel_safe_dark_pre == i)
  compare_paired(data=safe_i,
               var_name="feel_safe_dark",
               lgd_title=paste("Scores When Equal to ", i),
               plot_title="Paired: Feeling Safe When Dark")
}
```

### Reasons for Feeling Unsafe

```{r}
# What makes you feel the most unsafe?
# Unpaired
compare_pre_post(df_pre=initial_pre, df_post=post_clean, 
                 var_name="feel_unsafe_reasons", var_type="non_cont",
                 subplot_type="bar_simple", lgd_title = "Reasons",
                 title="Unpaired: Reasons for Feeling unsafe")

# Paired
compare_paired(data=paired_clean,
               var_name="feel_unsafe_reasons",
               lgd_title="Reasons",
               plot_title="Paired: Reasons for Feeling unsafe")

## Subgroup analysis using pre-survey reasons, what was their post-survey
```

```{r}
as.data.frame.matrix(table(paired_enc$feel_safe_levels_pre, 
                        paired_enc$feel_safe_levels_post)
            )
```

### Presence of Community Lights

```{r}
# Does your community currently have outdoor community lights?
# Unpaired
compare_pre_post(df_pre=initial_pre, df_post=post_clean, 
                 var_name="community_lights", var_type="non_cont",
                 subplot_type="bar_simple", 
                 lgd_title = "Present?",
                 title="Unpaired: Presence of Community Lights")

# Paired
generic_compare(data=paired_clean, var_type="non_cont",
               var1="community_lights_pre", 
               var2="community_lights_post", 
               lgd_title ="Present?",
               var1_title="Pre", var2_title="Post", 
               subplot_type="pie", 
               plot_title="Paired: Presence of Community Lights")

# Paired
compare_paired(data=paired_clean,
               var_name="community_lights",
               lgd_title="Present?",
               plot_title="Paired: Change in Presence of Community Lights")
```

### Household - Exterior Lights

```{r}
# Does your home have exterior lighting?
# Unpaired
compare_pre_post(df_pre=initial_pre, df_post=post_clean, 
                 var_name="home_exterior_lights", var_type="non_cont",
                 subplot_type="bar_simple", 
                 lgd_title = "Does the home have exterior lights?",
                 title="Unpaired: Presence of Home Exterior Lights")
# Paired
generic_compare(data=paired_clean, var_type="non_cont",
               var1="home_exterior_lights_pre", 
               var2="home_exterior_lights_post", 
               lgd_title ="Present?",
               var1_title="Pre", var2_title="Post", 
               subplot_type="bar_simple", 
               plot_title="Paired: Presence of Home Exterior Lights")

# Paired
compare_paired(data=paired_clean,
               var_name="home_exterior_lights",
               lgd_title="Does the home have exterior lights?",
               plot_title="Paired: Change in Presence of Home Exterior Lights")
```

### Exterior Lights By Mini-Grid

```{r}
# Is this exterior lighting powered by minigrid?
plot_func(df=post_clean, var_name="exterior_lights_minigrid", 
          var_type="non_cont", lgd="Powered by Mini-Grid",
          plot_title="Households - Exterior Lights Powered by Mini-Grid", 
          plot_type="bar_simple")
```

## B) Inferential

### TODO: Feeling Safe

**Data Source**: Paired Household Surveys (Pre & Post)

**Value (Encoding if applied)**: "Very unsafe" = 1; "Somewhat unsafe" = 2; "Neither safe nor unsafe"= 3; "Somewhat safe" = 4; "Very safe" = 5

#### TODO: Paired Test\*

```{r}
# # How safe do you feel outside your home when it is dark?
print("All")
paired_testing(paired_enc, var_name="feel_safe_dark", 
               test_type = "wilcoxon", plot_diff=TRUE, diff_type = "magnitude",
               #remove_outliers = TRUE, 
               threshold = 4, threshold_bound = "lower",
               x_axis="Differences", y_axis="Count",
               plt_title="All - Difference in Pre-Post Safety Scores")

## Subgroup Analysis - Country
# Nigeria
# print("Nigeria")
# ctr <- 1
# country_paired <- paired_enc %>% filter(country_post == ctr)
# paired_testing(country_paired, var_name="feel_safe_dark", 
#                test_type = "wilcoxon", plot_diff=TRUE,
#                diff_type = "magnitude",
#                #remove_outliers = TRUE, 
#                threshold = 4, threshold_bound = "lower",
#                x_axis="Differences", y_axis="Count",
#                plt_title="Nigeria - Difference in Pre-Post Safety Scores")
# # Kenya
# print("Kenya")
# ctr <- 2
# country_paired <- paired_enc %>% filter(country_post == ctr)
# paired_testing(country_paired, var_name="feel_safe_dark", 
#                test_type = "wilcoxon", plot_diff=TRUE,
#                diff_type = "magnitude",
#                #remove_outliers = TRUE, 
#                threshold = 4, threshold_bound = "lower",
#                x_axis="Differences", y_axis="Count",
#                plt_title="Kenya - Difference in Pre-Post Safety Scores")
```

### Unsafe Travel

**Data Source**: Paired Household Surveys (Pre & Post)

**Value (Encoding if applied)**: "Yes" = 1; "No" = 0

#### Paired Test\*

```{r}
paired_testing(paired_enc, var_name="unsafe_due_to_unsafe_travel", 
               test_type = "mcnemar", plot_diff=FALSE)
```

#### Regression - Community

```{r}
community_reg(df=paired_enc, 
              col_name="unsafe_due_to_unsafe_travel", dep="-1", 
              title="Decrease in Feeling Unsafe Due to Travel", 
              exclude_outliers = TRUE, outliers = "feature",
              var_type="categorical", calc_diff = TRUE,
              diff_type="direction", customer_type="hs", 
              y_axis= "Households",
              sig_var="Customers", unit_val = "HH/Cust", extra="")
```

#### Logistic Regression - Individual

```{r}
consumption_reg(df=paired_enc,  reg_type ="logistic",
                dep="unsafe_due_to_unsafe_travel", 
                ind="avg_mon_consumption_period",
                exclude_outliers = TRUE, outliers = "feature",
                calc_diff=TRUE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption Pre-Post Period (kWh)", 
                y_axis="Feeling Unsafe Change (Decrease)", log_direction = -1,
                title="Due To Travel vs. Consumption")
```

### Community Lighting

**Data Source**: Paired Household Surveys (Pre & Post)

**Value (Encoding if applied)**: "Yes" = 1; "No" = 0

#### Paired Test\*

```{r}
paired_testing(paired_enc, var_name="unsafe_due_to_lack_of_community_lighting", 
               test_type = "mcnemar", plot_diff=FALSE)
```

#### Regression - Community

```{r}
community_reg(df=paired_enc, 
              col_name="unsafe_due_to_lack_of_community_lighting", dep="-1", 
              title="Decrease in Feeling Unsafe Due to Lack of Community Lighting", 
              exclude_outliers = TRUE, outliers = "feature",
              var_type="categorical", calc_diff = TRUE,
              diff_type="direction", customer_type="hs", 
              y_axis= "Households",
              sig_var="Customers", unit_val = "HH/Cust", extra="")
```

#### Logistic Regression - Individual

```{r}
consumption_reg(df=paired_enc,  reg_type ="logistic",
                dep="unsafe_due_to_lack_of_community_lighting", 
                ind="avg_mon_consumption_period",
                exclude_outliers = TRUE, outliers = "feature",
                calc_diff=TRUE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption Pre-Post Period (kWh)", 
                y_axis="Feeling Unsafe Change (Decrease)", log_direction = -1,
                title="Due To Community Lighting vs. Consumption")
```

### Potential Theft

**Data Source**: Paired Household Surveys (Pre & Post)

**Value (Encoding if applied)**: "Yes" = 1; "No" = 0

#### TODO: Paired Test\*

```{r}
# Undesired outcome
paired_testing(paired_enc, var_name="unsafe_due_to_theft", 
               test_type = "mcnemar", plot_diff=FALSE)
```

#### Regression - Community

```{r}
# What makes you feel the most unsafe? Testing for Potentiel Theft only
community_reg(df=paired_enc, 
              col_name="unsafe_due_to_theft", dep="-1", 
              title="Decrease in Feeling Unsafe Due to Theft", 
              exclude_outliers = TRUE, outliers = "feature",
              var_type="categorical", calc_diff = TRUE,
              diff_type="direction", customer_type="hs", 
              y_axis= "Households",
              sig_var="Customers", unit_val = "HH/Cust", extra="")
```

#### Logistic Regression - Individual

```{r}
consumption_reg(df=paired_enc,  reg_type ="logistic",
                dep="unsafe_due_to_theft", 
                ind="avg_mon_consumption_period",
                exclude_outliers = TRUE, outliers = "feature",
                calc_diff=TRUE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption Pre-Post Period (kWh)", 
                y_axis="Feeling Unsafe Change (Increase)", log_direction = -1,
                title="Due To Theft vs. Consumption")
```

### Presence of House Exterior Lights\*

**Data Source**: Paired Household Surveys (Pre & Post)

**Value (Encoding if applied)**: "Yes" = 1; "No" = 0

#### Paired Test\*

```{r}
# Does your home have exterior lighting?
paired_testing(paired_enc, var_name="home_exterior_lights", 
               test_type = "mcnemar", plot_diff=FALSE)
```

#### Regression - Community

```{r}
community_reg(df=paired_enc, 
              col_name="home_exterior_lights", dep="1", 
              title="Increase in Home Exterior Lighting", 
              exclude_outliers = TRUE, outliers = "feature",
              var_type="categorical", calc_diff = TRUE,
              diff_type="direction", customer_type="hs", 
              y_axis= "Households",
              sig_var="Customers", unit_val = "HH/Cust", extra="")
```

#### Logistic Regression - Individual

```{r}
consumption_reg(df=paired_enc,  reg_type ="logistic",
                dep="home_exterior_lights", 
                ind="avg_mon_consumption_period",
                exclude_outliers = TRUE, outliers = "feature",
                calc_diff=TRUE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption Pre-Post Period (kWh)", 
                y_axis="Access Change (Increase)", log_direction = -1,
                title="Home Exterior Lighting vs. Consumption")
```

# 6- Economic Activity

## A) Descriptive

### Occupation Change

```{r}
# Has your (or your spouses) occupation changed since youve been connected to minigrid power?
plot_func(df=post_clean, var_name="occupation_change", 
          var_type="non_cont", lgd="Change in Occupation?",
          plot_title="Change in Occupation of Primary Provider", 
          plot_type="bar_simple")
```

### Household Income

#### Nigeria

```{r}
# What is your average monthly household income:
# Unpaired
ctr <- "nigeria"
country_pre <- initial_pre %>% filter(country == ctr)
country_post <- post_clean %>% filter(country == ctr)
compare_pre_post(df_pre=country_pre, df_post=country_post, 
                 var_name="avg_household_income", var_type="cont",
                 subplot_type="hist", shared_legend=FALSE,
                 exclude_outliers = TRUE,
                 x_axis="Value ( Naira)", y_axis="Count",
                 title="Unpaired: Nigeria - Average Household Income")
```

#### Kenya

```{r}
# Unpaired
test_df <- read.csv("data_cleaning/household_post_survey_anonymized.csv")
ctr <- "kenya"
country_pre <- initial_pre %>% filter(country == ctr)
country_post <- test_df %>% filter(country == ctr)
compare_pre_post(df_pre=country_pre, df_post=country_post, 
                 var_name="avg_household_income", var_type="cont",
                 subplot_type="hist", shared_legend=FALSE,
                 exclude_outliers = TRUE,
                 x_axis="Value (Ksh)", y_axis="Count",
                 char_remove = c(0),
                 title="Unpaired: Kenya - Average Household Income")
```

```{r}
# Paired
# compare_paired(data=kenya_post_enc,
#                var_name="avg_household_income",
#                lgd_title="Do you have clean drinking water?",
#                plot_title="Paired: Clean Drinking Water Sources")

generic_compare(data=kenya_paired_enc, var_type="cont", 
                var1="avg_household_income_pre", 
                var2="avg_household_income_post", 
               var1_title="Income-Pre", var2_title="Income-Post", 
                          subplot_type="hist", plot_title="",
                          lgd_title="", x_axis=NULL, y_axis=NULL,
                          char_remove=NULL)
```

### Household Income Change

```{r}
# Has your household income changed since your connection to minigrid power?
plot_func(df=kenya_post_enc, var_name="household_income_change", 
          var_type="non_cont", lgd="Change",
          plot_title="Change in Household Income", 
          plot_type="pie")

plot_func(df=nigeria_post_enc, var_name="household_income_change", 
          var_type="non_cont", lgd="Change",
          plot_title="Change in Household Income", 
          plot_type="pie")
```

### Household Expenses

#### Phone Charging

```{r}
# How much do you pay per month to charge your mobile phone?
# Unpaired
ctr <- "kenya"
country_pre <- initial_pre %>% filter(country == ctr)
country_post <- post_clean %>% filter(country == ctr)
compare_pre_post(df_pre=country_pre, df_post=country_post, 
                 var_name="phone_charge_cost", var_type="non_cont",
                 subplot_type="pie", lgd_title = "Costs",
                 title="Kenya Unpaired: Phone Charging Cost")

# Paired
paired_clean_country <- paired_clean %>% filter(country_pre == ctr)
compare_paired(data=paired_clean_country,
               var_name="phone_charge_cost",
               lgd_title="Costs",
               plot_title="Kenya Paired: Phone Charging Cost")


ctr <- "nigeria"
country_pre <- initial_pre %>% filter(country == ctr)
country_post <- post_clean %>% filter(country == ctr)
compare_pre_post(df_pre=country_pre, df_post=country_post, 
                 var_name="phone_charge_cost", var_type="non_cont",
                 subplot_type="pie", lgd_title = "Costs",
                 title="Nigeria - Unpaired: Phone Charging Cost")

# Paired
paired_clean_country <- paired_clean %>% filter(country_pre == ctr)
compare_paired(data=paired_clean_country,
               var_name="phone_charge_cost",
               lgd_title="Costs",
               plot_title="Nigeria - Paired: Phone Charging Cost")
```

#### Appliances Charging

```{r}
# What is approximate monthly cost of energy used strictly for charging appliances?
# Unpaired
ctr <- "kenya"
country_pre <- initial_pre %>% filter(country == ctr)
country_post <- post_clean %>% filter(country == ctr)
compare_pre_post(df_pre=country_pre, df_post=country_post,
                 var_name="applicances_charging_cost", var_type="non_cont",
                 subplot_type="pie", lgd_title = "Costs",
                 title="Kenya - Unpaired: Appliances Charging Cost")

# Paired
paired_clean_country <- paired_clean %>% filter(country_pre == ctr)
compare_paired(data=paired_clean_country,
               var_name="applicances_charging_cost",
               lgd_title="Costs",
               plot_title="Kenya - Paired: Appliances Charging Cost")

ctr <- "nigeria"
country_pre <- initial_pre %>% filter(country == ctr)
country_post <- post_clean %>% filter(country == ctr)
compare_pre_post(df_pre=country_pre, df_post=country_post,
                 var_name="applicances_charging_cost", var_type="non_cont",
                 subplot_type="pie", lgd_title = "Costs",
                 title="Nigeria - Unpaired: Appliances Charging Cost")

# Paired
paired_clean_country <- paired_clean %>% filter(country_pre == ctr)
compare_paired(data=paired_clean_country,
               var_name="applicances_charging_cost",
               lgd_title="Costs",
               plot_title="Nigeria - Paired: Appliances Charging Cost")
```

#### Cooking Energy

```{r}
# What is the approximate monthly cost of energy used strictly for cooking?
# Unpaired
ctr <- "kenya"
country_pre <- initial_pre %>% filter(country == ctr)
country_post <- post_clean %>% filter(country == ctr)
compare_pre_post(df_pre=country_pre, df_post=country_post,
                 var_name="cooking_energy_cost", var_type="non_cont",
                 subplot_type="pie", lgd_title = "Costs",
                 title="Kenya Unpaired: Cooking Energy Cost")

# Paired
paired_clean_country <- paired_clean %>% filter(country_pre == ctr)
compare_paired(data=paired_clean_country,
               var_name="cooking_energy_cost",
               lgd_title="Costs",
               plot_title="Kenya Paired: Cooking Energy Cost")

ctr <- "nigeria"
country_pre <- initial_pre %>% filter(country == ctr)
country_post <- post_clean %>% filter(country == ctr)
compare_pre_post(df_pre=country_pre, df_post=country_post,
                 var_name="cooking_energy_cost", var_type="non_cont",
                 subplot_type="pie", lgd_title = "Costs",
                 title="Nigeria Unpaired: Cooking Energy Cost")

# Paired
paired_clean_country <- paired_clean %>% filter(country_pre == ctr)
compare_paired(data=paired_clean_country,
               var_name="cooking_energy_cost",
               lgd_title="Costs",
               plot_title="Nigeria Paired: Cooking Energy Cost")
```

#### Water Cost

```{r}
# Unpaired
ctr <- "kenya"
country_pre <- initial_pre %>% filter(country == ctr)
country_post <- post_clean %>% filter(country == ctr)
compare_pre_post(df_pre=country_pre, df_post=country_post,
                 var_name="water_cost", var_type="non_cont",
                 subplot_type="pie", lgd_title = "Costs",
                 title="Kenya Unpaired: Water Cost")

# Paired
paired_clean_country <- paired_clean %>% filter(country_pre == ctr)
compare_paired(data=paired_clean_country,
               var_name="water_cost",
               lgd_title="Costs",
               plot_title="Kenya Paired: Water Cost")

ctr <- "nigeria"
country_pre <- initial_pre %>% filter(country == ctr)
country_post <- post_clean %>% filter(country == ctr)
compare_pre_post(df_pre=country_pre, df_post=country_post,
                 var_name="water_cost", var_type="non_cont",
                 subplot_type="pie", lgd_title = "Costs",
                 title="Nigeria Unpaired: Water Cost")

# Paired
paired_clean_country <- paired_clean %>% filter(country_pre == ctr)
compare_paired(data=paired_clean_country,
               var_name="water_cost",
               lgd_title="Costs",
               plot_title="Nigeria Paired: Water Cost")
```

#### Kerosene Lamps

```{r}
# How much do you pay monthly for kerosene used only in kerosene lamps?
# # Unpaired
# compare_pre_post(df_pre=initial_pre, df_post=post_clean, 
#                  var_name="kerosene_lamps_cost", var_type="non_cont",
#                  subplot_type="bar_simple", lgd_title = "Costs",
#                  title="Unpaired: Kerosene Lamps Cost")
# 
# # Paired
# compare_paired(data=paired_clean,
#                var_name="kerosene_lamps_cost",
#                lgd_title="Costs",
#                plot_title="Paired: Kerosene Lamps Cost")


ctr <- "kenya"
country_pre <- initial_pre %>% filter(country == ctr)
country_post <- post_clean %>% filter(country == ctr)
compare_pre_post(df_pre=country_pre, df_post=country_post,
                 var_name="kerosene_lamps_cost", var_type="non_cont",
                 subplot_type="pie", lgd_title = "Costs",
                 title="Kenya Unpaired: Kerosene Lamps Cost")

# Paired
paired_clean_country <- paired_clean %>% filter(country_pre == ctr)
compare_paired(data=paired_clean_country,
               var_name="kerosene_lamps_cost",
               lgd_title="Costs",
               plot_title="Kenya Paired: Kerosene Lamps Cost")

ctr <- "nigeria"
country_pre <- initial_pre %>% filter(country == ctr)
country_post <- post_clean %>% filter(country == ctr)
compare_pre_post(df_pre=country_pre, df_post=country_post,
                 var_name="kerosene_lamps_cost", var_type="non_cont",
                 subplot_type="pie", lgd_title = "Costs",
                 title="Nigeria Unpaired: Kerosene Lamps Cost")

# Paired
paired_clean_country <- paired_clean %>% filter(country_pre == ctr)
compare_paired(data=paired_clean_country,
               var_name="kerosene_lamps_cost",
               lgd_title="Costs",
               plot_title="Nigeria Paired: Kerosene Lamps Cost")
```

### Local Business Creation

#### Business Owners

```{r}
# Are any household members business owners?
# Unpaired
compare_pre_post(df_pre=initial_pre, df_post=post_clean, 
                 var_name="business_owners_binary", var_type="non_cont",
                 subplot_type="bar_simple", lgd_title = "Own a Business?",
                 title="Unpaired: Household Business Ownership")
# Paired
generic_compare(data=paired_clean, var_type="non_cont",
               var1="business_owners_binary_pre", 
               var2="business_owners_binary_post", 
               lgd_title ="Own a Business?",
               var1_title="Pre", var2_title="Post", 
               subplot_type="bar_simple", 
               plot_title="Paired: Household Business Ownership")
# Paired
compare_paired(data=paired_clean,
               var_name="business_owners_binary",
               lgd_title="Own a Business?",
               plot_title="Paired: Change in Household Business Ownership")
```

#### Recently Open

```{r}
# Is this business recent (started after connection to minigrid power?)
plot_func(df=post_clean, var_name="business_recent", 
          var_type="non_cont", lgd="Recent?",
          plot_title="Recent Business Ownership", 
          plot_type="bar_simple")
```

#### Mini-grid related

```{r}
# If this business is new, do you consider this new business a result of having access to minigrid power?
plot_func(df=post_clean, var_name="business_use_minigrid", 
          var_type="non_cont", lgd="Recent?",
          plot_title="Business, A Result From Mini-Grid", 
          plot_type="bar_simple")
```

### C&I

#### bv Operation Status

```{r}
# Is this business, clinic, school still in operation?
plot_func(df=ci_clean, var_name="operation_status", 
          var_type="non_cont", lgd = "Status",
          plot_title="C&I - Type", 
          plot_type="pie")
```

#### Business Type

```{r}
# Please select your business type
plot_func(df=ci_clean, var_name="business_type", 
          var_type="non_cont", lgd = "Business Type",
          plot_title="C&I - Type", 
          plot_type="pie")
```

#### Earnings Change

```{r}
plot_func(df=ci_clean, var_name="earnings_change", 
          var_type="non_cont", lgd = "Change in Earnings?",
          plot_title="C&I - Type", 
          plot_type="pie")
```

## B) Inferential

### Avg. Household Income - Nigeria

**Data Source**: Paired Household Surveys (Pre & Post)

**Value (Encoding if applied)**: Any numeric value

#### TODO: Paired Testing\*

```{r}
unique(nigeria_paired_clean$avg_household_income_post)
```

```{r}
## What is your average monthly household income? 
ctr <- "nigeria"

paired_testing(nigeria_paired_clean, var_name="avg_household_income",
               test_type = "ttest", plot_diff=TRUE, 
               #remove_outliers = TRUE,
               x_axis="Value ( Naira)", y_axis="Count",
               plt_title="Nigeria - Income Differences")
```

```{r}
community_reg(df=nigeria_paired_enc, 
              col_name="avg_household_income", dep="1", 
              title="Household Income Increase by Community", 
              exclude_outliers = TRUE, outliers = "feature",
              var_type="categorical", calc_diff = TRUE,
              diff_type="direction", customer_type="hs", 
              y_axis= "Households",
              sig_var="Customers", unit_val = "HH/Cust", extra="")
```

#### Linear Regression - Individual\*

```{r}
consumption_reg(df = post_enc, reg_type ="linear",
                dep= "avg_household_income", ind="avg_mon_consumption_period",
                #calc_diff=TRUE, diff_type = "magnitude",
                x_axis="Avg. Monthly Energy Consumption Pre-Post Period (kwH)", 
                y_axis="Income ( Naira)", 
                exclude_outliers = TRUE, outliers = "dependent",
                #threshold = 0, threshold_bound = "lower",
                title="Avg. Household Income vs Consumption")
```

#### Logistic Regression - Individual

```{r}
consumption_reg(df=nigeria_paired_enc,  reg_type ="logistic",
                dep="avg_household_income", 
                ind="avg_mon_consumption_period",
                exclude_outliers = TRUE, outliers = "feature",
                calc_diff=TRUE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption Pre-Post Period (kWh)", 
                y_axis="Income (Increase)", log_direction = 1,
                title="Avg. Household Income vs. Consumption")

consumption_reg(df=nigeria_paired_enc,  reg_type ="logistic",
                dep="avg_household_income", 
                ind="avg_mon_consumption_period",
                exclude_outliers = TRUE, outliers = "feature",
                calc_diff=TRUE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption Pre-Post Period (kWh)", 
                y_axis="Income (Decrease)", log_direction = -1,
                title="Avg. Household Income vs. Consumption")
```

### Avg. Household Income - Kenya

**Data Source**: Paired Household Surveys (Pre & Post)

**Value (Encoding if applied)**: Any numeric value

#### TODO: Paired Testing\*

```{r}
median(kenya_paired_enc$avg_household_income_pre, na.rm = T)
```

```{r}

paired_testing(kenya_paired_enc, var_name="avg_household_income", 
               test_type = "ttest", plot_diff=TRUE,
               #remove_outliers = TRUE,
               x_axis="Value (Ksh)", y_axis="Count",
               plt_title="Kenya - Income Differences")
```

#### Regression - Community

```{r}
community_reg(df=kenya_paired_enc, 
              col_name="avg_household_income", dep="1", 
              title="Household Income Increase by Community", 
              exclude_outliers = TRUE, outliers = "feature",
              var_type="categorical", calc_diff = TRUE,
              diff_type="direction", customer_type="hs", 
              y_axis= "Households Reporting Increase",
              sig_var="Customers", unit_val = "HH/Cust", extra="")
```

#### Linear Regression - Individual

```{r}
#kenya_temp <- kenya_paired_enc %>% filter(avg_mon_consumption_period < 2)
consumption_reg(df=kenya_paired_enc,  reg_type ="linear",
                dep="avg_household_income", 
                ind="avg_mon_consumption_cum",
                exclude_outliers = TRUE, outliers = "dependent",
                calc_diff=TRUE, diff_type = "magnitude",
                x_axis="Avg. Monthly Energy Consumption Cumulative (kWh)", 
                y_axis="Income (Increase)", 
                title="Avg. Household Income vs. Consumption")
```

### Household - Income Change

**Data Source**: Household Post Survey

**Value (Encoding if applied)**: "Yes, it's decreased" = -1; "No, it's the same" = 0; "Yes, it's increased" = 1

#### Regression - Community

```{r}
## Has your household income changed since your connection to mini-grid power?
community_reg(df=post_enc, 
              col_name="household_income_change", dep="1", 
              title="Household Income Increase by Community", 
              exclude_outliers = TRUE, outliers = "feature",
              var_type="categorical", calc_diff = FALSE,
              diff_type="direction", customer_type="hs", 
              y_axis= "Households",
              sig_var = "PV_Size_kWp", unit_val = "Orgs/kWp", extra="")
```

```{r}
nigeria_post_enc <- post_enc %>% filter(country == 1)
community_reg(df=nigeria_post_enc, 
              col_name="household_income_change", dep="1", 
              title="Nigeria - Household Income Increase by Community", 
              exclude_outliers = TRUE, outliers = "feature",
              var_type="categorical", calc_diff = FALSE,
              diff_type="direction", customer_type="hs", 
              y_axis= "Households",
              title_sig="Increase of Avg. Household Income in Nigerian Communities") 
```

```{r}
kenya_post_enc <- post_enc %>% filter(country == 2)
community_reg(df=kenya_post_enc, 
              col_name="household_income_change", dep="1", 
              title="Kenya - Household Income Increase by Community", 
              exclude_outliers = TRUE, outliers = "feature",
              var_type="categorical", calc_diff = FALSE,
              diff_type="direction", customer_type="hs", 
              y_axis= "Households", 
                title="Avg. Household Income vs. Consumption")
```

#### Logistic Regression - Individual

```{r}
consumption_reg(df=post_enc,  reg_type ="logistic",
                dep="household_income_change", 
                ind="avg_mon_consumption_cum",
                exclude_outliers = TRUE, outliers = "feature",
                #calc_diff=TRUE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption Cumulative (kWh)", 
                y_axis="Change (Increase)", log_direction = 1,
                title="Household Income vs. Consumption")
```

```{r}
consumption_reg(df=nigeria_post_enc,  reg_type ="logistic",
                dep="household_income_change", 
                ind="avg_mon_consumption_cum",
                exclude_outliers = TRUE, outliers = "feature",
                #calc_diff=TRUE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption Cumulative (kWh)", 
                y_axis="Change (Increase)", log_direction = 1,
                title="Nigeria - Household Income vs. Consumption")
```

### C&I - Earnings Change

**Data Source**: Household Post Survey

**Value (Encoding if applied)**: "Yes, it's decreased" = -1; "No, it's the same" = 0; "Yes, it's increased" = 1

#### Regression - Community\*

```{r}
# For businesses or shop owners only: Since connection to Renewvia mini-grid, have you seen any change in your weekly or monthly earnings?
community_reg(df=ci_enc, 
              col_name="earnings_change", dep="1", 
              title="C&I Earnings Increase by Community", 
              exclude_outliers = TRUE, outliers = "feature",
              var_type="categorical", calc_diff = FALSE,
              diff_type="direction", customer_type="ci", 
              y_axis= "Organizations \nReporting Increase",
              sig_var = "PV_Size_kWp", unit_val = "Orgs/kWp", extra=""
              #title_sig="Increase of Earnings for Organizations in Communities"
              )
```

#### Logistic Regression - Individual

```{r}
consumption_reg(df=ci_enc,  reg_type ="logistic",
                dep="earnings_change", 
                ind="avg_mon_consumption_cum",
                exclude_outliers = TRUE, outliers = "feature",
                #calc_diff=TRUE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption Cumulative (kWh)", 
                y_axis="Change (Increase)", log_direction = 1,
                title="Earnings vs. Consumption")
```

```{r}
nigeria_ci_enc <- ci_enc %>% filter(country == 1)
consumption_reg(df=nigeria_ci_enc,  reg_type ="logistic",
                dep="earnings_change", 
                ind="avg_mon_consumption_cum",
                exclude_outliers = TRUE, outliers = "feature",
                #calc_diff=TRUE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption Cumulative (kWh)", 
                y_axis="Change (Increase)", log_direction = 1,
                title="Nigeria - C&I Earnings vs. Consumption")
```

```{r}
kenya_ci_enc <- ci_enc %>% filter(country == 2)
consumption_reg(df=kenya_ci_enc,  reg_type ="logistic",
                dep="earnings_change", 
                ind="avg_mon_consumption_cum",
                exclude_outliers = TRUE, outliers = "feature",
                #calc_diff=TRUE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption Cumulative (kWh)", 
                y_axis="Change (Increase)", log_direction = 1,
                title="Nigeria - C&I Earnings vs. Consumption")
```

### Business Ownership

**Data Source**: Paired Household Surveys (Pre & Post)

**Value (Encoding if applied)**: "None" = 0; "Not None" = 1

#### Paired Test\*

```{r}
# Are any household members business owners?
paired_testing(paired_enc, var_name="business_owners_binary", 
               test_type = "mcnemar", plot_diff=FALSE)
```

#### Regression - Community\*

```{r}
community_reg(df=paired_enc, 
              col_name="business_owners_binary", dep="1", 
              title="Household Business Onwership by Community", 
              exclude_outliers = TRUE, outliers = "feature",
              var_type="categorical", calc_diff =TRUE,
              diff_type="direction", customer_type="hs", 
              y_axis= "Households",
              sig_var = "PV_Size_kWp", unit_val = "Orgs/kWp", extra="")
```

#### Logistic Regression - Individual

```{r}
consumption_reg(df=paired_enc,  reg_type ="logistic",
                dep="business_owners_binary", 
                ind="avg_mon_consumption_period",
                exclude_outliers = TRUE, outliers = "feature",
                calc_diff=TRUE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption Pre-Post Period (kWh)", 
                y_axis="Change (Increase)", log_direction = 1,
                title="Business Ownership vs. Consumption")
```

### Phone Charging Cost

**Data Source**: Paired Household Surveys (Pre & Post)

**Value (Encoding if applied)**: "Nothing" = 0; "0_100_nkes" = 1, "100_500_nkes" = 2, "500_750_nkes": 3, "750_1000_nkes" = 4, "1000_nkes_and_above" = 5, "1000_n_and_above" = 5

#### TODO: Paired Test\*

```{r}
paired_testing(paired_enc, var_name="phone_charge_cost", 
               test_type = "wilcoxon", x_axis="Differences", y_axis="Count",
               plt_title="Difference in Pre-Post Phone Charging Cost",
               plot_diff=TRUE, 
               #remove_outliers = TRUE
               )
```

#### Paired Test by Country

```{r}
# Phone Charging
# Nigeria
print("Nigeria")
paired_testing(nigeria_paired_enc, var_name="phone_charge_cost", 
               test_type = "sign", x_axis="Differences", y_axis="Count",
               plt_title="Nigeria: Difference in Pre-Post Phone Charging Cost",
               plot_diff=TRUE,  
               #remove_outliers = TRUE
               )

# Kenya
print("Kenya")
paired_testing(kenya_paired_enc, var_name="phone_charge_cost", 
               test_type = "sign", x_axis="Differences", y_axis="Count",
               plt_title="Kenya: Difference in Pre-Post Phone Charging Cost",
               plot_diff=TRUE, 
               #remove_outliers = TRUE
               )
```

#### Regression - Community by Country

```{r}
# ctr <- 1
# country_df <- paired_enc %>% filter(country_post == ctr)
community_reg(df=nigeria_paired_enc, 
              col_name="phone_charge_cost", dep="-1", 
              title="Phone Charging Cost Savings by Community", 
              exclude_outliers = TRUE, outliers = "feature",
              var_type="categorical", calc_diff = TRUE,
              diff_type="direction", customer_type="hs", 
              y_axis= "Households",
              sig_var="Customers", unit_val = "HH/Cust", extra="")
```

```{r}
community_reg(df=kenya_paired_enc, 
              col_name="phone_charge_cost", dep="-1", 
              title="Phone Charging Cost Savings by Community", 
              exclude_outliers = TRUE, outliers = "feature",
              var_type="categorical", calc_diff = TRUE,
              diff_type="direction", customer_type="hs", 
              y_axis= "Households",
              sig_var="Customers", unit_val = "HH/Cust", extra="")
```

#### Logistic Regression - Individual

```{r}
consumption_reg(df=paired_enc,  reg_type ="logistic",
                dep="phone_charge_cost", 
                ind="avg_mon_consumption_period",
                exclude_outliers = TRUE, outliers = "feature",
                calc_diff=TRUE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption Pre-Post Period (kWh)", 
                y_axis="Change (Decrease)", log_direction = -1,
                title="Phone Charging Cost vs. Consumption")
```

### Appliance Charging Cost

**Data Source**: Paired Household Surveys (Pre & Post)

**Value (Encoding if applied)**: "nothing" = 0, "0_150_nkes" = 1, "150_1000_nkes" = 2, "1000_3000_nkes" = 3, "3000_4000_nkes" = 4, "4000_6000_nkes" = 5

#### Paired Test\*

```{r}
paired_testing(paired_enc, var_name="applicances_charging_cost", 
               test_type = "wilcoxon", x_axis="Differences", y_axis="Count",
               plt_title="Difference in Pre-Post Appliances Charging Cost",
               plot_diff=TRUE, 
               remove_outliers = TRUE
               )
```

#### Paired Test by Country\*

```{r}
# Nigeria
paired_testing(nigeria_paired_enc, var_name="applicances_charging_cost", 
               test_type = "sign", x_axis="Differences", y_axis="Count",
               plt_title="Nigeria: Difference in Pre-Post Appliances Charging Cost",
               plot_diff=TRUE, 
               #remove_outliers = TRUE
               )


# Kenya
paired_testing(kenya_paired_enc, var_name="applicances_charging_cost", 
               test_type = "sign", x_axis="Differences", y_axis="Count",
               plt_title="Kenya: Difference in Pre-Post Appliances Charging Cost",
               plot_diff=TRUE, 
               #remove_outliers = TRUE
)
```

#### Regression - Community

```{r}
community_reg(df=paired_enc, 
              col_name="applicances_charging_cost", dep="-1", 
              title="Appliance Charging Cost Savings by Community", 
              exclude_outliers = TRUE, outliers = "feature",
              var_type="categorical", calc_diff = TRUE,
              diff_type="direction", customer_type="hs", 
              y_axis= "Households")
```

```{r}
community_reg(df=nigeria_paired_enc, 
              col_name="applicances_charging_cost", dep="-1", 
              title="Phone Charging Cost Savings by Community", 
              exclude_outliers = TRUE, outliers = "feature",
              var_type="categorical", calc_diff = TRUE,
              diff_type="direction", customer_type="hs", 
              y_axis= "Households",
              sig_var="Customers", unit_val = "HH/Cust", extra="")
```

```{r}
community_reg(df=kenya_paired_enc, 
              col_name="applicances_charging_cost", dep="-1", 
              title="Phone Charging Cost Savings by Community", 
              exclude_outliers = TRUE, outliers = "feature",
              var_type="categorical", calc_diff = TRUE,
              diff_type="direction", customer_type="hs", 
              y_axis= "Households",
              sig_var="Customers", unit_val = "HH/Cust", extra="")
```

#### Logistic Regression - Individual

```{r}
consumption_reg(df=paired_enc,  reg_type ="logistic",
                dep="applicances_charging_cost", 
                ind="avg_mon_consumption_period",
                exclude_outliers = TRUE, outliers = "feature",
                calc_diff=TRUE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption Pre-Post Period (kWh)", 
                y_axis="Change (Decrease)", log_direction = -1,
                title="Appliances Charging Cost vs. Consumption")
```

### Cooking Energy Cost

**Data Source**: Paired Household Surveys (Pre & Post)

**Value (Encoding if applied)**: "nothing" = 0, "0_1000_nkes" = 1, "1000_1500_nkes" = 2, "1500_2000_nkes" = 3, "2000_3000_nkes" = 4, "3000_4000_nkes" = 5

#### Paired Test\*

```{r}
paired_testing(paired_enc, var_name="cooking_energy_cost", 
               test_type = "wilcoxon", x_axis="Differences", y_axis="Count",
               plt_title="Difference in Pre-Post Appliances Charging Cost",
               plot_diff=TRUE, 
               remove_outliers = TRUE
               )
```

#### Paired Test by Country\*

```{r}
# Nigeria
paired_testing(nigeria_paired_enc, var_name="cooking_energy_cost", 
               test_type = "wilcoxon", x_axis="Differences", y_axis="Count",
               plt_title="Nigeria: Difference in Pre-Post Cooking Energy Cost",
               plot_diff=TRUE, 
               remove_outliers = TRUE,
               #threshold = 4, threshold_bound = "lower",
               )


# Kenya
paired_testing(kenya_paired_enc, var_name="cooking_energy_cost", 
               test_type = "wilcoxon", x_axis="Differences", y_axis="Count",
               plt_title="Kenya: Difference in Pre-Post Cooking Energy Cost",
               plot_diff=TRUE, 
               remove_outliers = TRUE
               )
```

#### Regression - Community

```{r}
community_reg(df=paired_enc, 
              col_name="cooking_energy_cost", dep="-1", 
              title="Cooking Energy Cost Savings by Community", 
              exclude_outliers = TRUE, outliers = "feature",
              var_type="categorical", calc_diff = TRUE,
              diff_type="direction", customer_type="hs", 
              y_axis= "Households")
```

```{r}
community_reg(df=nigeria_paired_enc, 
              col_name="cooking_energy_cost", dep="-1", 
              title="Cooking Energy Cost Savings by Community", 
              exclude_outliers = TRUE, outliers = "feature",
              var_type="categorical", calc_diff = TRUE,
              diff_type="direction", customer_type="hs", 
              y_axis= "Households",
              sig_var="Customers", unit_val = "HH/Cust", extra="")
```

```{r}
community_reg(df=kenya_paired_enc, 
              col_name="cooking_energy_cost", dep="-1", 
              title="Cooking Energy Cost Savings by Community", 
              exclude_outliers = TRUE, outliers = "feature",
              var_type="categorical", calc_diff = TRUE,
              diff_type="direction", customer_type="hs", 
              y_axis= "Households",
              sig_var="Customers", unit_val = "HH/Cust", extra="")
```

#### Logistic Regression - Individual

```{r}
consumption_reg(df=paired_enc,  reg_type ="logistic",
                dep="cooking_energy_cost", 
                ind="avg_mon_consumption_period",
                exclude_outliers = TRUE, outliers = "feature",
                calc_diff=TRUE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption Pre-Post Period (kWh)", 
                y_axis="Change (Decrease)", log_direction = -1,
                title="Cooking Energy Cost vs. Consumption")
```

### Kerosene Lamps Cost

**Data Source**: Paired Household Surveys (Pre & Post)

**Value (Encoding if applied)**: "nothing" = 0,"0_200_nkes" = 1,"200_600_nkes" = 2,"600_1000_nkes" = 3,"1000_1400_nkes" = 4,"1400_nkes_and_above" = 5

#### Paired Test\*

```{r}
paired_testing(paired_enc, var_name="kerosene_lamps_cost", 
               test_type = "wilcoxon", x_axis="Differences", y_axis="Count",
               plt_title="Difference in Pre-Post Kerosene Lamps Cost",
               plot_diff=TRUE, 
               #remove_outliers = TRUE
               )
```

#### Paired Test by Country

```{r}
# Nigeria
paired_testing(nigeria_paired_enc, var_name="kerosene_lamps_cost", 
               test_type = "sign", x_axis="Differences", y_axis="Count",
               plt_title="Nigeria: Difference in Pre-Post Kerosene Lamps Cost",
               plot_diff=TRUE, 
               #remove_outliers = TRUE
               )


# Kenya
paired_testing(kenya_paired_enc, var_name="kerosene_lamps_cost", 
               test_type = "sign", x_axis="Differences", y_axis="Count",
               plt_title="Kenya: Difference in Pre-Post Kerosene Lamps Cost",
               plot_diff=TRUE, 
               #remove_outliers = TRUE
               )
```

#### Regression - Community

```{r}
community_reg(df=paired_enc, 
              col_name="kerosene_lamps_cost", dep="-1", 
              title="Kerosene Lamps Cost Savings by Community", 
              exclude_outliers = TRUE, outliers = "feature",
              var_type="categorical", calc_diff = TRUE,
              diff_type="direction", customer_type="hs", 
              y_axis= "Households",
              sig_var="Customers", unit_val = "HH/Cust", extra="")
```

```{r}
community_reg(df=nigeria_paired_enc, 
              col_name="kerosene_lamps_cost", dep="-1", 
              title="Kerosene Lamps Cost Savings by Community", 
              exclude_outliers = TRUE, outliers = "feature",
              var_type="categorical", calc_diff = TRUE,
              diff_type="direction", customer_type="hs", 
              y_axis= "Households",
              sig_var="Customers", unit_val = "HH/Cust", extra="")
```

```{r}
community_reg(df=kenya_paired_enc, 
              col_name="kerosene_lamps_cost", dep="-1", 
              title="Kerosene Lamps Cost Savings by Community", 
              exclude_outliers = TRUE, outliers = "feature",
              var_type="categorical", calc_diff = TRUE,
              diff_type="direction", customer_type="hs", 
              y_axis= "Households",
              sig_var="Customers", unit_val = "HH/Cust", extra="")
```

#### Logistic Regression - Individual

```{r}
consumption_reg(df=paired_enc,  reg_type ="logistic",
                dep="kerosene_lamps_cost", 
                ind="avg_mon_consumption_period",
                exclude_outliers = TRUE, outliers = "feature",
                calc_diff=TRUE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption Pre-Post Period (kWh)", 
                y_axis="Change (Decrease)", log_direction = -1,
                title="Kerosene Lamps Cost vs. Consumption")
```

### Water Cost

**Data Source**: Paired Household Surveys (Pre & Post)

**Value (Encoding if applied)**: "nothing" = 0, "0_500_nkes" = 1, "500_3000_nkes" = 2, "3000_5000_nkes" = 3, "5000_nkes_and_above" = 4

#### Paired Test\*

```{r}
paired_testing(paired_enc, var_name="water_cost", 
               test_type = "wilcoxon", x_axis="Differences", y_axis="Count",
               plt_title="Nigeria: Difference in Pre-Post Water Cost",
               plot_diff=TRUE, 
               #remove_outliers = TRUE
               )
```

#### Paired Test by Country\*

```{r}
# Nigeria
paired_testing(nigeria_paired_enc, var_name="water_cost", 
               test_type = "sign", x_axis="Differences", y_axis="Count",
               plt_title="Nigeria: Difference in Pre-Post Water Cost",
               plot_diff=TRUE, 
               #remove_outliers = TRUE
               )


# Kenya
paired_testing(kenya_paired_enc, var_name="water_cost", 
               test_type = "wilcoxon", x_axis="Differences", y_axis="Count",
               plt_title="Kenya: Difference in Pre-Post Water Cost",
               plot_diff=TRUE, 
               #remove_outliers = TRUE
               )
```

#### Regression - Community\*

```{r}
community_reg(df=paired_enc, 
              col_name="water_cost", dep="-1", 
              title="Water Cost Savings by Community", 
              exclude_outliers = TRUE, outliers = "feature",
              var_type="categorical", calc_diff = TRUE,
              diff_type="direction", customer_type="hs", 
              y_axis= "Households",
              sig_var="Customers", unit_val = "HH/Cust", extra="")
```

```{r}
community_reg(df=nigeria_paired_enc, 
              col_name="water_cost", dep="-1", 
              title="Water Cost Savings by Community", 
              exclude_outliers = TRUE, outliers = "feature",
              var_type="categorical", calc_diff = TRUE,
              diff_type="direction", customer_type="hs", 
              y_axis= "Households",
              sig_var="Customers", unit_val = "HH/Cust", extra="")
```

```{r}
community_reg(df=kenya_paired_enc, 
              col_name="water_cost", dep="-1", 
              title="Water Cost Savings by Community", 
              exclude_outliers = TRUE, outliers = "feature",
              var_type="categorical", calc_diff = TRUE,
              diff_type="direction", customer_type="hs", 
              y_axis= "Households",
              sig_var="Customers", unit_val = "HH/Cust", extra="")
```

#### Logistic Regression - Individual

```{r}
consumption_reg(df=paired_enc,  reg_type ="logistic",
                dep="water_cost", 
                ind="avg_mon_consumption_period",
                exclude_outliers = TRUE, outliers = "feature",
                calc_diff=TRUE, diff_type = "direction",
                x_axis="Avg. Monthly Energy Consumption Pre-Post Period (kWh)", 
                y_axis="Change (Decrease)", log_direction = -1,
                title="Water Cost vs. Consumption")
```

## Visualize Significant Results

### Gender Equality

```{r}
new_legend <- c("Pre-Connection","One Year \nPost-Connection")
```

```{r, fig.width=4, fig.height=4}
# Gender Equality
cols <- c("renewvia_id")
var_names <- c("water_collection_time", 
                      "cooking_fuel_collection_time"
                      )
for(var in var_names) {
  pre_name <- paste(var, "pre", sep="_")
  post_name <- paste(var, "post", sep="_")
  cols <- c(cols,pre_name, post_name)
}

test_paired <- paired_enc[, cols]
# Split the data in two groups
#test_paired <- outliers_removal(test_paired, pre_name)
#test_paired <- outliers_removal(test_paired, post_name)
test_paired_longer <- test_paired %>%
                              pivot_longer(
                                cols = -renewvia_id,
                                #names_to = "when",
                                # names_prefix = var_name,
                                # values_to = var_name,
                                # values_drop_na = TRUE,
                                # names_transform = list(var_name = as.numeric)
                                names_to = c(".value","Period"), 
                                names_pattern =  "(\\w+)_(pre|post)"
                              )
#test_paired_longer
#var_norm <- paste(var_name, "normalized", sep="_")
test_paired_longer[, var_names] <- normalize(test_paired_longer[, var_names])
box_data <- test_paired_longer  %>%
                        pivot_longer(
                          cols = -c("renewvia_id", "Period"),
                          #names_to = "when",
                          # names_prefix = var_name,
                          # values_to = var_name,
                          # values_drop_na = TRUE,
                          # names_transform = list(var_name = as.numeric)
                          names_to = c("var"), 
                          #names_pattern =  "(\\w+)_(pre|post)"
                        )
# re_names <- c(`water_collection_time` = "Water Collection Time",
#               `cooking_fuel_collection_time` = "Cooking Fuel Collection Time")
re_names <- c(
  `water_collection_time` = "Water \nCollection Time", 
  `cooking_fuel_collection_time` = "Cooking Fuel \nCollection Time"
                    )
box_data$Period <- factor(box_data$Period , levels=c("pre", "post"))
box_plot <- box_data %>% ggplot(aes(x = Period, 
                                    y = value, fill=Period)) + 
                        geom_violin(bw= 0.25, adjust=0.75,
                                    position = position_dodge(),
                                     outlier.shape = NA) +
                        labs(y="Normalized\n Value"
                             #title = "Gender Equality - Paired Testing Results"
                             ) + 
                        facet_grid(~factor(var,
                                           levels=var_names),
                                   labeller = as_labeller(re_names),
                                   switch = "both") + 
                        theme_classic() +
                        scale_fill_manual(name="", 
                                          values=c("#ef641e", "#87CEEB"),
                                          labels=new_legend) +
                        theme(legend.position = 'top', 
                       legend.text=element_text(size=12),
                       strip.background = element_blank(),
                       strip.text = element_text(size = 12),
                       axis.text=element_text(size=12), #change font size of axis text
                       axis.title=element_text(size=12),
                       strip.placement = "outside") +
                        remove_x 


box_plot <- box_plot + draw_line(
                    x = c(0),
                    y = c(0, 1),
                    color = "grey", size = .5
                                )

ggsave("gender_equality_paired_results.pdf", box_plot,
       width = 4, height = 4, dpi = 400, device='pdf')
box_plot 
```

### Productivity

```{r, fig.width=6, fig.height=6}
# Productivity
cols <- c("renewvia_id")
var_names <- c("light_hours_current", 
                "appliances_count",
                "phone_charge_travel_distance",
                "water_collection_travel_distance"
                )
for(var in var_names) {
  pre_name <- paste(var, "pre", sep="_")
  post_name <- paste(var, "post", sep="_")
  cols <- c(cols,pre_name, post_name)
}

test_paired <- paired_enc[, cols]
# Split the data in two groups
#test_paired <- outliers_removal(test_paired, pre_name)
#test_paired <- outliers_removal(test_paired, post_name)
test_paired_longer <- test_paired %>%
                              pivot_longer(
                                cols = -renewvia_id,
                                #names_to = "when",
                                # names_prefix = var_name,
                                # values_to = var_name,
                                # values_drop_na = TRUE,
                                # names_transform = list(var_name = as.numeric)
                                names_to = c(".value","Period"), 
                                names_pattern =  "(\\w+)_(pre|post)"
                              )
#test_paired_longer
#var_norm <- paste(var_name, "normalized", sep="_")
test_paired_longer[, var_names] <- normalize(test_paired_longer[, var_names])
box_data <- test_paired_longer  %>%
                        pivot_longer(
                          cols = -c("renewvia_id", "Period"),
                          #names_to = "when",
                          # names_prefix = var_name,
                          # values_to = var_name,
                          # values_drop_na = TRUE,
                          # names_transform = list(var_name = as.numeric)
                          names_to = c("var"), 
                          #names_pattern =  "(\\w+)_(pre|post)"
                        )
re_names <- c(
  `light_hours_current` = "Light Hours", 
  `appliances_count` = "No. of \nAppliances", 
  `phone_charge_travel_distance` = "Phone Charging\n Distance",
  `water_collection_travel_distance` = "Water Collection\n Distance"
                    )
box_data$Period <- factor(box_data$Period , levels=c("pre", "post"))
box_plot <- box_data %>% ggplot(aes(x = Period, 
                                    y = value, fill=Period)) + 
                        geom_boxplot(position = position_dodge(),
                                     outlier.shape = NA) +
                        labs(y="Normalized \nValue"
                             #title = "Productivity - Paired Testing Results"
                             ) + 
                        facet_grid(~factor(var,
                                           levels=var_names),
                                   labeller = as_labeller(re_names),
                                   switch = "both") + 
                        theme_classic() +
                        scale_fill_manual(name="",
                                          values=c("#ef641e", "#87CEEB"),
                                          labels=new_legend) +
                        theme(legend.position = 'top', 
                       legend.text=element_text(size=12),
                       strip.background = element_blank(),
                       strip.text = element_text(size = 12),
                       axis.text=element_text(size=12), #change font size of axis text
                       axis.title=element_text(size=12),
                       strip.placement = "outside") + 
  remove_x

ggsave("productivity_paired_results.pdf", box_plot,
       width = 6, height = 6, dpi = 600, device='pdf')
box_plot 
```

### Health

```{r}
# Health
cols <- c("renewvia_id")
var_names <- c("kerosene_lamps_count"
                )
for(var in var_names) {
  pre_name <- paste(var, "pre", sep="_")
  post_name <- paste(var, "post", sep="_")
  cols <- c(cols,pre_name, post_name)
}

test_paired <- paired_enc[, cols]
# Split the data in two groups
#test_paired <- outliers_removal(test_paired, pre_name)
#test_paired <- outliers_removal(test_paired, post_name)
test_paired_longer <- test_paired %>%
                              pivot_longer(
                                cols = -renewvia_id,
                                #names_to = "when",
                                # names_prefix = var_name,
                                # values_to = var_name,
                                # values_drop_na = TRUE,
                                # names_transform = list(var_name = as.numeric)
                                names_to = c(".value","Period"), 
                                names_pattern =  "(\\w+)_(pre|post)"
                              )
#test_paired_longer
#var_norm <- paste(var_name, "normalized", sep="_")
test_paired_longer[, var_names] <- normalize(test_paired_longer[, var_names])
box_data <- test_paired_longer  %>%
                        pivot_longer(
                          cols = -c("renewvia_id", "Period"),
                          #names_to = "when",
                          # names_prefix = var_name,
                          # values_to = var_name,
                          # values_drop_na = TRUE,
                          # names_transform = list(var_name = as.numeric)
                          names_to = c("var"), 
                          #names_pattern =  "(\\w+)_(pre|post)"
                        )
#re_names <- c(`water_collection_time` = "Water Collection Time",
              #`cooking_fuel_collection_time` = "Cooking Fuel Collection Time")
re_names <- c(
  `kerosene_lamps_count` = "No. of Kerosene Lamps"
                    )
box_data$Period <- factor(box_data$Period , levels=c("pre", "post"))
box_plot <- box_data %>% ggplot(aes(x = Period, 
                                    y = value, fill=Period)) + 
                        geom_boxplot(position = position_dodge(),
                                     outlier.shape = NA) +
                        labs(y="Normalized \nValue" 
                             #title = "Health - Paired Testing Results"
                             ) + 
                        facet_grid(~factor(var,
                                           levels=var_names),
                                   labeller = as_labeller(re_names),
                                   switch = "both") + 
                        theme_classic() +
                        scale_fill_manual(name="",
                                          values=c("#ef641e", "#87CEEB"),
                                          labels=new_legend) +
                        theme(legend.position = 'top', 
                       legend.text=element_text(size=12),
                       strip.background = element_blank(),
                       strip.text = element_text(size = 12),
                       axis.text=element_text(size=12), #change font size of axis text
                       axis.title=element_text(size=12),
                       strip.placement = "outside") + remove_x
box_plot <- box_plot + draw_line(
                    x = c(0),
                    y = c(0, 1),
                    color = "grey", size = .5
                                )
ggsave("health_paired_results.pdf", box_plot,
       width = 4, height = 4, dpi = 400, device='pdf')
box_plot 
```

### Economic Activity

```{r, fig.width=7, fig.height=7}
# Economic Activity
# Nigeria
nigeria_paired_incomes <- nigeria_paired_enc[, c("renewvia_id",
                                                 "avg_household_income_pre",
                                                "avg_household_income_post")]
names(nigeria_paired_incomes)[names(nigeria_paired_incomes) == "avg_household_income_pre"] <- "avg_household_income_nigeria_pre"
names(nigeria_paired_incomes)[names(nigeria_paired_incomes) == "avg_household_income_post"] <- "avg_household_income_nigeria_post"

# Kenya
kenya_paired_incomes <- kenya_paired_enc[, c("renewvia_id",
                                                 "avg_household_income_pre",
                                                "avg_household_income_post")]
names(kenya_paired_incomes)[names(kenya_paired_incomes) == "avg_household_income_pre"] <- "avg_household_income_kenya_pre"
names(kenya_paired_incomes)[names(kenya_paired_incomes) == "avg_household_income_post"] <- "avg_household_income_kenya_post"


paired_merged <- merge(x=paired_enc,y=kenya_paired_incomes, 
                    by="renewvia_id", all.x=TRUE)
paired_merged <- merge(x=paired_merged,y=nigeria_paired_incomes, 
                    by="renewvia_id", all.x=TRUE)

cols <- c("renewvia_id")
var_names = c("phone_charge_cost",
              "applicances_charging_cost",
              "cooking_energy_cost", 
              "kerosene_lamps_cost",
              "water_cost",
              "avg_household_income_nigeria",
              "avg_household_income_kenya"
                      )
for(var in var_names) {
  pre_name <- paste(var, "pre", sep="_")
  post_name <- paste(var, "post", sep="_")
  cols <- c(cols,pre_name, post_name)
}
test_paired <- paired_merged[, cols]

test_paired_longer <- test_paired %>%
                              pivot_longer(
                                cols = -renewvia_id,
                                #names_to = "when",
                                # names_prefix = var_name,
                                # values_to = var_name,
                                # values_drop_na = TRUE,
                                # names_transform = list(var_name = as.numeric)
                                names_to = c(".value","Period"), 
                                names_pattern =  "(\\w+)_(pre|post)"
                              )
test_paired_longer[, var_names] <- normalize(test_paired_longer[, var_names])
box_data <- test_paired_longer  %>%
                        pivot_longer(
                          cols = -c("renewvia_id", "Period"),
                          names_to = c("var"), 
                          #names_pattern =  "(\\w+)_(pre|post)"
                        )

re_names <- c(
  # `light_hours_current` = "Light Hours", 
  # `appliances_count` = "No. of Appliances", 
  # `phone_charge_travel_distance` = "Phone Charging Distance",
  `phone_charge_cost` = "Phone \nCharge \nCost",
  `applicances_charging_cost` = "Appliance \nCharge \nCost",
  `cooking_energy_cost` = "Cooking \nEnergy \nCost", 
  `kerosene_lamps_cost` = "Kerosene \nLamps \nCost",
  `water_cost` = "Water \nCost",
  `avg_household_income_nigeria` = "Nigeria \nIncomes",
  `avg_household_income_kenya` = "Kenya \nIncomes"
                    )
box_data$Period <- factor(box_data$Period , levels=c("pre", "post"))
box_plot <- box_data %>% ggplot(aes(x = Period, 
                                    y = value, fill=Period)) + 
                        geom_boxplot(position = position_dodge(),
                                     outlier.shape = NA) +
                        labs(y="Normalized Value"
                             #title = "Economic Activity - Paired Testing Results"#
                             ) + 
                        facet_grid(~factor(var,
                                           levels=var_names),
                                   labeller = as_labeller(re_names),
                                   switch = "both") + 
                        theme_classic() +
                        scale_fill_manual(name="",
                                          values=c("#ef641e", "#87CEEB"),
                                          labels=new_legend) +
                        theme(legend.position = 'top', 
                       legend.text=element_text(size=12),
                       strip.background = element_blank(),
                       strip.text = element_text(size = 12),
                       axis.text=element_text(size=12),
                       axis.title=element_text(size=12),
                       strip.placement = "outside") + remove_x
box_plot <- box_plot + draw_line(
                    x = c(0),
                    y = c(0, 1),
                    color = "grey", size = .5
                                )

ggsave("economic_activity_paired_results.pdf", box_plot,
       width = 7, height = 7, dpi = 700, device='pdf')
box_plot  
```

### Title figure

```{r, fig.width=6, fig.height=6}
#Title figure 
cols <- c("renewvia_id")
var_names = c("cooking_fuel_collection_time",
                      "light_hours_current",
                      "kerosene_lamps_count",
                      "phone_charge_cost"
                      )
for(var in var_names) {
  pre_name <- paste(var, "pre", sep="_")
  post_name <- paste(var, "post", sep="_")
  cols <- c(cols,pre_name, post_name)
}
test_paired <- paired_merged[, cols]

test_paired_longer <- test_paired %>%
                              pivot_longer(
                                cols = -renewvia_id,
                                #names_to = "when",
                                # names_prefix = var_name,
                                # values_to = var_name,
                                # values_drop_na = TRUE,
                                # names_transform = list(var_name = as.numeric)
                                names_to = c(".value","Period"), 
                                names_pattern =  "(\\w+)_(pre|post)"
                              )
test_paired_longer[, var_names] <- normalize(test_paired_longer[, var_names])
box_data <- test_paired_longer  %>%
                        pivot_longer(
                          cols = -c("renewvia_id", "Period"),
                          names_to = c("var"), 
                          #names_pattern =  "(\\w+)_(pre|post)"
                        )

re_names <- c(
  `cooking_fuel_collection_time` = "Cooking Fuel \nCollection Time",
  `light_hours_current` = "Light Hours", 
  # `appliances_count` = "No. of Appliances", 
  # `phone_charge_travel_distance` = "Phone Charging Distance",
  `kerosene_lamps_count` = "No. of \nKerosene Lamps",
  `phone_charge_cost` = "Phone \nCharging Cost"
                    )
box_data$Period <- factor(box_data$Period , levels=c("pre", "post"))
par(ps=12)
box_plot <- box_data %>% ggplot(aes(x = Period, 
                                    y = value, fill=Period)) + 
                        geom_boxplot(position = position_dodge(),
                                     outlier.shape = NA) +
                        labs(y="Normalized Value" 
                             #title = "Economic Activity - Paired Testing Results"
                        ) + 
                        facet_grid(~factor(var,
                                           levels=var_names),
                                   labeller = as_labeller(re_names),
                                   switch = "both") + 
                        theme_classic() +
                        scale_fill_manual(name="",
                                          values=c("#ef641e", "#87CEEB"),
                                          labels=new_legend) +
                        theme(legend.position = 'top', 
                       legend.text=element_text(size=12),
                       strip.background = element_blank(),
                       strip.text = element_text(size = 12),
                       axis.text=element_text(size=12),
                       axis.title=element_text(size=12),
                       strip.placement = "outside") + remove_x

box_plot <- box_plot + draw_line(
                    x = c(0),
                    y = c(0, 1),
                    color = "grey", size = .5
                                )

ggsave("title_figure_paired_results.pdf", box_plot,
       width = 6, height = 6, dpi = 600, device='pdf')
box_plot 
```
